\section{Background}

\subsection{Offline-Peek Calibration as Upper Bound}

Paper~5~\cite{paper5temporal} introduced an offline-peek calibration
ablation as a methodological control: at each window $w$, grid-search
the scorer weights $(\alpha, \beta, \gamma, \delta)$ on the
calibration seeds at \textit{window~$w$ state} to maximise mean P@50,
then apply the fitted weights to the evaluation seeds at the same
window~$w$. The procedure peeks at the window it is scoring; it
establishes an upper bound on what any deployable procedure could
achieve, but it is not itself deployable.

The K=50, $\lambda=3$ cell-mean improvement from offline-peek over
fixed weights was $+21.3$~pp at W2 and remained positive through W4.
Whether this margin survives the lag a deployable procedure must
impose is the question this paper asks.

\subsection{Rolling-History Calibration}

The simplest deployable substitute uses only past observations: at
window $w$, fit weights on calibration-seed data at windows
$\{1, \ldots, w-1\}$. The narrowest such procedure --- lag-1 --- uses
only window $w-1$. Longer histories (multi-window smoothing) trade
variance for bias under distributional shift. The pre-registration
discipline applied throughout this paper locks the procedural
parameters before evaluation.

\subsection{Change-Point Detection}

When the distribution shifts faster than the calibration history can
track, a richer alternative is to detect the shift directly and gate
the recalibration decision. The simplest detector is a magnitude test
on the calibration-target shift $|\Delta_w|$; the classical alternative
is CUSUM~\cite{page1954cusum}, which accumulates positive deviations
and fires when the accumulator crosses a threshold $h$. Both
classes are evaluated here under pre-registered parameter locks.

\subsection{Capacity-Conditional Operation}

Paper~6~\cite{paper6capacity} documented that HygienePrio's absolute
P@50 floor collapses at $K \in \{100, 200\}$ under the simulated
bi-weekly cadence. The collapse is a property of the residual
backlog at high capacity, not of the scoring weights, and bounds
the maximum value any recalibration procedure can deliver at those
capacities. The capacity-conditional structure motivates the
per-K parameter vectors evaluated in E5 and the per-K conclusion in
the deployable recipe.

\subsection{Selection-Policy Coupling}

A separate methodological concern is that, under the multi-window
fleet-evolution policy that Papers~5--6 use, the selection policy
that drives the fleet trajectory affects the residual backlog that
later methods are scored against. Paper~9~\cite{paper9selftraj}
quantified this coupling and showed it can re-attribute the K=200
absolute collapse from an intrinsic scoring property to a
selection-policy artifact. The present paper inherits the
fixed-trajectory convention (HygienePrio-full under fixed weights
drives the fleet for all strategies in every experiment) and bounds
its claims accordingly; selection-policy coupling is restated as an
internal-validity threat in \S\ref{sec:threats}.

\subsection{Policy Mandates}

CISA BOD 22-01~\cite{cisa2021bod2201} and 23-01~\cite{cisa2022bod2301}
together with NIST SP 800-40 Rev.~4~\cite{nist2022sp80040r4} define
the operational rolling-window scheduling regime under which any
recalibration procedure must operate. The CUSUM and capacity-aware
$\tau$ detectors evaluated here are auditable in a way that
gradient-based and Bayesian alternatives are not.
