\section{Problem Formulation}
\label{sec:problem}

\subsection{Setting (Inherited)}

EEHDA synthetic fleet (Paper~4)~\cite{paper4hygieneprio}, Paper~5
multi-window simulator~\cite{paper5temporal}, capacity $K$ pairs
remediated per window, $\lambda$ Poisson new-CVE arrivals per window,
$W = 6$ windows. The HygienePrio scorer and HRS components are
inherited verbatim:
\begin{equation}
\begin{aligned}
S(h,c) =\;& \alpha\,\mathrm{EPSS}(c) + \beta\,\mathrm{HRS}(h) \\
          & + \gamma\,\mathrm{KEV\_recency}(c) \\
          & + \delta\,\bigl(\mathrm{EPSS}(c) \cdot \mathrm{HRS}(h)\bigr).
\end{aligned}
\label{eq:hp}
\end{equation}
Only the four scorer weights are subject to recalibration; HRS
weights are not.

\subsection{Six Pre-Registered Experiments}

Each experiment locks a procedure and a hypothesis set before any
evaluation-seed P@50 is inspected:

\textbf{E1 --- Lag-1 online.} At $w \geq 2$, grid-search weights on
calibration seeds at $w - 1$; apply at $w$. Comparators: \textsf{fixed},
\textsf{offline-peek} (Paper 5 H3 ceiling).

\textbf{E2 --- Multi-window smoothing.} Same grid-search but
aggregated across multiple past windows: \textsf{trail3} (equal
weights over $\max(1, w-3)..w-1$); \textsf{ewma3} (geometric weights,
$\alpha = 0.6$). Comparators add \textsf{lag1}.

\textbf{E3 --- Single-$\tau$ adaptive.} At $w \geq 2$, compute the
calibration-target shift $\Delta_w$ on the lag-1-fit weights between
two consecutive past windows. Fire if $|\Delta_w| \geq \tau$
($\tau = 0.05$). On fire, revert to fixed weights for window $w$;
otherwise use the lag-1-fit weights. Comparator: static gate
($K \leq 100 \to$ lag1; $K \geq 200 \to$ fixed).

\textbf{E4 --- $\tau$ sensitivity sweep.} E3 with
$\tau \in \{0.02, 0.03, 0.05, 0.075, 0.10\}$. Reports H1/H2 Pareto
curve.

\textbf{E5 --- Capacity-aware $\tau$.} Same detector as E3 but with
a pre-registered per-K threshold vector $\tau_K = \{50: 0.20,
100: 0.05, 200: 0.02\}$ locked from inspection of E4 calibration-seed
shift distribution.

\textbf{E6 --- One-sided CUSUM.} Accumulator $C_w = \max(0, C_{w-1}
+ |\Delta_w| - k)$ with $C_1 = 0$. Fire if $C_w \geq h$, then reset.
Pre-registered $k = 0.04$, $h = 0.10$.

\subsection{Ground Truth and Primary Metric}

Inherited from Papers~5--6: a pair $(h, c)$ is a positive at
window $w$ if EPSS$(c) > 0.10$, HRS$(h)$ exceeds the fleet's 75th
percentile at $w$, and $(h, c) \in V_w$. The HRS threshold is
recomputed per window. P@50 is the primary metric.

\subsection{Pre-Registered Hypotheses}

The full ledger of 27 hypotheses (4--5 per experiment) is in
Table~\ref{tab:hypothesis_ledger}, page~\pageref{tab:hypothesis_ledger}.
Each hypothesis was locked before the corresponding experiment's
evaluation-seed P@50 was inspected; per-experiment decision rules
and stop rules are archived in the per-experiment protocol files.
