\section{Methodology}

\subsection{Grid Search}

Every experiment that fits weights does so via a 108-point grid
search over $(\alpha, \beta, \gamma, \delta) \in \{0.5, 0.7, 0.9\}
\times \{0.3, 0.5, 0.7\} \times \{0.0, 0.1, 0.2\} \times \{0.0, 0.1,
0.2, 0.3\}$, identical to Paper~5's recalibration ablation.

\subsection{Per-Experiment Procedures}

\textbf{E1 lag-1.} At $w \geq 2$, the grid search is performed on
the calibration seeds at window $w - 1$ to maximise mean P@50.

\textbf{E2 smoothing.} The fitting objective generalises to:
$\bar p(g) = \sum_{i \in H} w_i\,p_i(g) / \sum_i w_i$
where $H \subseteq \{1, \ldots, w-1\}$ and $w_i$ are pre-registered
weights. For \textsf{trail3}: $H = \{\max(1, w-3), \ldots, w-1\}$,
equal weights. For \textsf{ewma3}: same $H$, geometric weights
$\alpha^i$ with $\alpha = 0.6$.

\textbf{E3 adaptive ($\tau = 0.05$).} Compute the calibration-target
shift $\Delta_w = p^{\text{cal}}_{w-1}(g^{\textsf{lag1}}_w) -
p^{\text{ref}}_w$, where $p^{\text{ref}}_w$ is the same lag-1-fit
applied to window $w - 2$ ($w \geq 3$) or fixed-weight calibration
P@50 at $w - 1$ ($w = 2$). Fire if $|\Delta_w| \geq \tau$. On fire,
revert to Paper~4 fixed weights; otherwise apply $g^{\textsf{lag1}}_w$.

\textbf{E4 $\tau$ sweep.} Same as E3 with
$\tau \in \{0.02, 0.03, 0.05, 0.075, 0.10\}$. $\Delta_w$, the
lag-1-fit weights, and the offline-peek weights are
$\tau$-independent, so they are computed once per (cell, window)
and reused across $\tau$ values.

\textbf{E5 capacity-aware $\tau$.} Same E3 procedure but with
$\tau_K = \{50: 0.20, 100: 0.05, 200: 0.02\}$ instead of a single
$\tau$. The vector is locked from inspection of E4's
calibration-seed change-point decision log only --- no evaluation-seed
inspection.

\textbf{E6 CUSUM.} Accumulator $C_w = \max(0, C_{w-1} + |\Delta_w|
- k)$ with $C_1 = 0$. On fire ($C_w \geq h$), revert to fixed
weights for window $w$ and reset $C_w = 0$. Otherwise apply the
lag-1-fit weights. Pre-registered $k = 0.04$, $h = 0.10$.

\subsection{Comparators}

Every experiment includes \textsf{fixed} (Paper~4 weights) and
\textsf{offline-peek} (Paper~5 H3 ceiling, peek at the current
window's calibration state). E3--E6 additionally include
\textsf{gated} (static $K \leq 100 \to$ lag1; $K \geq 200 \to$
fixed) as a non-adaptive control. The static gate has no
per-window decision and serves as the deployable baseline that
any adaptive procedure must beat.

\subsection{Selection-Policy Convention}

HygienePrio-full under fixed weights drives the top-$K$ selection
at every window for every strategy in every experiment. The
recalibration decision affects the scoring weights only; the fleet
trajectory is shared. This isolates the recalibration decision from
the trajectory-generation decision; the trade-off is that the
adaptive procedures are evaluated against a trajectory their own
weights did not produce.

\subsection{Reporting Convention}

Cell-mean point estimates are means across 25 evaluation seeds.
95\% confidence intervals are percentile bootstrap with 10{,}000
resamples~\cite{efron1994introduction}. Spearman correlations
underlying H1.E4, H2.E4, H3.E5, H4.E4 are computed on small samples
(3 or 5 points) and are reported as point estimates rather than
strong inferential claims. No null-hypothesis significance tests
are reported; hypothesis decisions follow the pre-registered
tolerance thresholds.
