\section{Experimental Setup}

\subsection{Pre-Registration Discipline}

Each experiment was governed by a pre-registration document
(\texttt{paper7/experiments/0X\_*/PROTOCOL.md}) that locked the
procedure parameters, the hypothesis set, the decision rules, and
the stop rules \textit{before} the corresponding evaluation-seed
P@50 was inspected. The protocols and their lock dates are:

All six protocols are archived under
\texttt{paper7/experiments/0[1-6]\_*/} (locked dates: E1--E5
2026-06-04; E6 2026-06-05).

The sequence in which the protocols were locked matches the
narrative order: each later experiment's protocol was finalised
\textit{after} the previous experiment's evaluation rejected one or
more of its hypotheses. The honest contribution of this paper is
the chain of pre-registered rejections that drove the experimental
design.

\subsection{Per-Experiment Execution}

For each $K \in \{50, 100, 200\}$: cache per-window
$(\text{pairs}_w, \text{HRS}_w)$ states for the calibration and
evaluation seeds under fixed-weight HygienePrio-full trajectory;
per window, fit \textsf{lag1} and \textsf{offline} weights and
compute the experiment's procedure-specific decisions; score all 25
evaluation seeds at each window with each strategy's resulting
weights; persist one P@50 row per (seed, window, strategy).

\subsection{Statistical Reporting}

95\% percentile bootstrap CIs (10{,}000 resamples). Spearman tests
on small samples are reported as point estimates. Hypothesis
decisions follow pre-registered tolerance thresholds; no
NHST is reported.

\subsection{Reproducibility}

Each experiment is independently reproducible from its frozen seed
list via the runner in its own \texttt{src/} subdirectory. The
per-experiment README files document the invocation; all six
runners follow the pattern \texttt{PYTHONPATH=src python3 src/run\_*.py}.

Each runner re-uses Paper~5's window simulator and Paper~4's scorer
via \texttt{sys.path} injection; no code duplication. Determinism
is inherited from the per-(seed, window, step) RNG seeding.
