\section{Results}
\label{sec:results}

All numerical claims trace to the per-experiment frozen CSVs in
\texttt{paper7/experiments/0X\_*/results/}. The complete
hypothesis-outcome ledger across all six experiments is in
Table~\ref{tab:hypothesis_ledger}.

\input{tables/tab_hypothesis_ledger}

\subsection{E1 --- Lag-1 Online Recalibration}

The lag-1 procedure recovers the offline-peek ceiling at moderate
capacity and harms performance at high capacity.

\textbf{Per-cell recovery ratios} (over $w \geq 2$):
\[\rho_{K=50} = 1.04, \quad \rho_{K=100} = 0.99, \quad
\rho_{K=200} = -0.66.\]

At $K = 50, w = 2$ lag-1 produces P@50 $= 0.741$ against the
offline-peek ceiling of $0.757$ (and fixed-weight baseline $0.544$),
recovering $92.5\%$ of the offline gain without future-data leakage.
At $K = 200$ the procedure produces $-5.9$~pp at W2 and $-7.8$~pp
at W3 relative to fixed weights; the per-window calibration target
shifts faster than the lag-1 history can track.

\textbf{H1.E1 rejected} (two cell-windows fail the $-0.01$ tolerance
at $K = 200, w \in \{2, 3\}$). \textbf{H2.E1 rejected in the opposite
direction} (online sometimes exceeds offline-peek by $+1$ to $+3$~pp
at late windows; the five-seed offline grid search overfits).
\textbf{H3.E1 rejected} (at $K = 200$ the W4--W6 recovery does not
meet the $\geq 5$~pp absolute threshold).

The honest substantive interpretation: lag-1 is deployable and
recovers essentially the full offline ceiling at $K \leq 100$;
it incurs $-5.9$ to $-7.8$~pp losses at $K = 200$ in the first
two operating windows.

\subsection{E2 --- Multi-Window Smoothing}

The pre-registered prior was that averaging across more past windows
would reduce calibration-target variance and reverse the K=200
hazard. The data falsifies this prior.

\textbf{Per-cell recovery ratios:} EWMA-3 produces
$\rho_{50} = 0.53$, $\rho_{100} = -1.37$, $\rho_{200} = -0.94$.
\textsf{trail3} produces qualitatively similar values. Smoothing
\textit{worsens} the hazard at K=200 (worse than lag-1's $-0.66$)
and \textit{degrades} the K=50 and K=100 recovery (worse than
lag-1's $1.04$ and $0.99$).

\textbf{All four E2 hypotheses rejected} (H1.E2 EWMA-no-hazard;
H2.E2 EWMA-matches-lag1; H3.E2 EWMA-equals-trail3; H4.E2 EWMA-recovery).
The mechanism is bias-variance: under fast distributional shift,
older calibration windows are systematically less representative of
the target window than the most recent past, and averaging
introduces bias from those older states. The bias term dominates
the variance reduction.

The result rules out simple history-based smoothing as a fix for
the lag-1 K=200 hazard, motivating the change-point detection
class of E3--E6.

\subsection{E3 --- Single-$\tau$ Adaptive ($\tau = 0.05$)}

The magnitude detector at $\tau = 0.05$ avoids the K=200 hazard but
incurs a K=50 cost.

\textbf{H1.E3 supported.} At $K = 200$, adaptive's mean
$\Delta_{\text{adaptive}-\text{fixed}} = +0.7$~pp; no window incurs
a loss exceeding the $-0.01$ pre-registered tolerance.
\textit{First procedure in the sequence to avoid the K=200 hazard.}

\textbf{H4.E3 supported.} Adaptive beats the static gate at K=200 by
$+0.7$~pp cell-mean.

\textbf{H2.E3 rejected.} At K=50, the detector fires in $60\%$ of
post-W1 windows and the cell-mean delta vs lag-1 is $-5.3$~pp.
Adaptive trades moderate-capacity recovery for high-capacity safety.

\textbf{H3.E3 rejected.} Fire fractions $\{60\%, 40\%, 80\%\}$ at
$K \in \{50, 100, 200\}$ are non-monotone (Spearman $\rho = 0.5$).
The detector responds to per-window calibration-target dynamics, not
to capacity directly.

\subsection{E4 --- $\tau$ Sensitivity Sweep}

The sweep over $\tau \in \{0.02, 0.03, 0.05, 0.075, 0.10\}$ produces
\textbf{the central negative result of the program} on the
simple-detector branch.

\textbf{H3.E4 rejected.} \textit{No $\tau$ in the swept grid
simultaneously satisfies both pre-registered tolerances}
(worst K=200 delta $\geq -0.01$ AND cell-mean K=50 delta $\geq -0.02$).
The K=50 cost is between $-4.1$ and $-5.3$~pp at every $\tau$,
always exceeding the $-2.0$~pp ceiling. The Pareto curve over $\tau$
sits entirely outside the joint feasibility region.

\textbf{H1.E4 substantively strengthened.} The worst per-window K=200
adaptive--fixed delta is exactly $0.0$ at every $\tau$ tested ---
stronger than the single-$\tau$ H1.E3 result.

\textbf{H2.E4 and H4.E4 sign-direction rejected.} The
pre-registration predicted larger $\tau$ would fire more and incur
more K=50 cost. Mathematically the opposite holds: larger $\tau$
requires a larger shift to trigger and therefore fires less.
Spearman$(\tau, \text{fire frac}) = -0.97$ ($p = 0.005$). The
pre-registration encoded the wrong directional intuition; the
data direction is the substantive scientific claim.

E4 closes the simple-magnitude-detector branch with a sharp negative
feasibility result.

\subsection{E5 --- Capacity-Aware $\tau$}

A pre-registered per-K threshold vector
$\tau_K = \{50: 0.20, 100: 0.05, 200: 0.02\}$ reaches the joint
feasibility region for the first time in the program --- but does so
by collapsing to the static gate at the capacity extremes.

\textbf{H1.E5 supported.} All three tolerances are simultaneously met:
worst K=200 cap--fix $= 0$, cell-mean K=50 cap--lag1 $= 0.0$ exactly
(the large $\tau_{50} = 0.20$ never fires, so cap\_aware $=$ lag1
at every K=50 window), cell-mean K=100 cap--lag1 $= -0.004$.

\textbf{H3.E5 supported.} Fire fractions $\{0\%, 40\%, 100\%\}$ at
$K \in \{50, 100, 200\}$ give Spearman $\rho = 1.0$.

\textbf{H4.E5 rejected.} cap\_aware K=200 cell mean equals gated K=200
cell mean to four decimal places: $0.2664 = 0.2664$. The small
$\tau_{200}$ fires at every K=200 post-W1 window, so cap\_aware
reverts to fixed at every window --- the same decision the static
gate makes unconditionally at K=200. The per-window detector
contributes nothing beyond the static gate.

\textbf{Substantive interpretation.} E5 reaches feasibility by
\textit{approximating the static gate} at both capacity extremes:
at K=50 cap\_aware $=$ lag1 $=$ gated; at K=200 cap\_aware $=$
fixed $=$ gated. Only K=100 differs and the difference is within
noise. The static gate is the substantive recommendation at this
point in the program; capacity-aware $\tau$ validates the gate
without improving on it.

\subsection{E6 --- One-Sided CUSUM}

CUSUM with pre-registered $k = 0.04$, $h = 0.10$ is the first
detector in the program that \textit{beats} the static gate at
K=200 by an operationally meaningful margin.

\textbf{H4.E6 supported.} CUSUM K=200 cell mean $= 0.2754$;
cap\_aware K=200 cell mean $= 0.2664$; gated K=200 cell mean
$= 0.2664$. CUSUM is $+0.9$~pp above both.

\textbf{H3.E6 supported.} CUSUM fires at K=200 in $60\%$ of post-W1
windows; cap\_aware fires in $100\%$. The K=200 fire pattern is
$\{W2, W3, W6\}$. At W4 ($|\Delta| = 0.020$) and W5 ($|\Delta|
= 0.096$ after a $0.020$ predecessor that emptied the accumulator)
CUSUM does \textit{not} fire and uses the lag-1 fit, which is
beneficial. This is exactly the mechanism E5's static-collapse
result motivated.

\textbf{H2.E6 fine-margin rejected.} The pre-registered binary test
required cusum $-$ gated $\geq +0.01$. The observed margin is
$+0.0090$, missing the threshold by $0.001$~pp. We report the
rejection honestly and the substantive direction (CUSUM strictly
beats the gate by an operationally meaningful margin) as the
contribution.

\textbf{H1.E6 rejected.} At K=50, CUSUM fires in $20\%$ of post-W1
windows (vs cap\_aware's $0\%$). The cell-mean cusum--lag1 falls to
$-3.9$~pp, missing the $-2.0$~pp feasibility tolerance. A single
$(k, h)$ pair that wins at K=200 also fires harmfully at K=50; a
per-K $(k_K, h_K)$ vector is the natural fix and is left as future
work.

\subsection{Cross-Experiment Summary}

\input{tables/tab_summary}

The cumulative arc is operationally clear: lag-1 (E1) covers
$K \leq 100$; CUSUM (E6) is the only deployable procedure that
beats the static gate at K=200. Across $K \leq 100$ the static gate
suffices and the calibration arc reduces to the simple ``use lag-1
below the threshold'' recipe; at $K = 200$ CUSUM adds $+0.9$~pp
over the gate, the only operationally meaningful gain in the
entire program.

\subsection{Pre-Registration Deviations}

None. Each experiment's pre-registered procedure parameters,
hypotheses, decision rules, and stop rules were applied verbatim.
The H2.E1 sign reversal (online beats offline at some windows),
the E2 universal rejections, the E4 H2/H4 sign-direction
falsifications, the E5 static-gate collapse, and the E6 fine-margin
H2 rejection were all reported as observed.
