\section{Related Work}

\textbf{Offline-peek baseline.} Paper~5~\cite{paper5temporal}
established the offline-peek H3 ablation that this paper uses as
the upper-bound comparator across all six experiments.

\textbf{Capacity-conditional performance.}
Paper~6~\cite{paper6capacity} identified $K \in \{100, 200\}$ as
the regime where fixed-weight HygienePrio-full's absolute P@50
floor collapses. The present paper takes that collapse as the
problem statement and evaluates whether any deployable
recalibration procedure mitigates it.

\textbf{EPSS dynamics.} Jacobs et al.~\cite{jacobs2021epss,
jacobs2020improving} demonstrated the per-CVE exploit-likelihood
scoring framework that the HygienePrio scorer integrates. Ravalico
et al.~\cite{ravalico2025epsstemporal} studied per-CVE EPSS score
drift; neither study addresses online recalibration of the
\textit{integrating} scorer's weights.

\textbf{Change-point detection.} CUSUM~\cite{page1954cusum} is the
classical one-sided change-point detector. Two-sided CUSUM,
EWMA-CUSUM, Bayesian online change-point detection, and the
recent literature on adaptive concept-drift detection are out of
scope for this paper, which evaluates the simplest-deployable end
of the detector design space under pre-registration.

\textbf{Online learning for security signals.} Online learning
under distributional shift is a large area in machine learning.
The narrow question here --- deployability of a magnitude or
CUSUM detector applied to an integrating vulnerability-prioritization
scorer with calibration-grid weight fitting --- does not require
the literature's more sophisticated machinery and is not
surveyed in depth.

\textbf{Self-trajectory evaluation.}
Paper~9~\cite{paper9selftraj} addresses the cross-method
trajectory-coupling concern that the present paper inherits as
an internal-validity threat. The two papers are complementary:
Paper~9 quantifies the bias the fixed-trajectory convention
introduces; the present paper conditions on that convention to
isolate the recalibration decision.

\textbf{HygieneBench and HygienePrio foundations.}
HygieneBench (Paper~3)~\cite{paper3hygienebench},
HygienePrio (Paper~4)~\cite{paper4hygieneprio}, and Temporal
Stability (Paper~5)~\cite{paper5temporal} provide the scorer,
simulator, and seed split that all six experiments here inherit.

\textbf{Policy mandates.} CISA BOD~22-01~\cite{cisa2021bod2201},
23-01~\cite{cisa2022bod2301}, NIST SP~800-40
Rev.~4~\cite{nist2022sp80040r4}, and the 2026
DBIR~\cite{verizon2026dbir} define the operational rolling-window
scheduling regime under which the procedures must operate.
