\section{Conclusion}
\label{sec:conclusion}

A pre-registered evaluation of rolling-history online calibration for
hygiene-augmented vulnerability prioritization across three capacity
levels, six windows, three calibration strategies, and 25 evaluation
seeds produces 1{,}350 result rows that revise the operational
recommendation implied by Paper~5's offline-peek ablation.

\textbf{First}, at moderate capacity ($K \leq 100$), the deployable
lag-1 rolling-history grid search recovers essentially all of the
offline-peek gain (cell-mean recovery ratio $\rho = 1.04$ at
$K = 50$, $\rho = 0.99$ at $K = 100$). At $K = 50, w = 2$ the procedure
adds $+19.7$~pp over fixed Paper~4 weights, against the offline
ceiling of $+21.3$~pp. Deployable online recalibration is operationally
viable in this regime.

\textbf{Second}, at high capacity ($K = 200$), lag-1 rolling-history
online recalibration \textit{harms} performance: $-5.9$ to
$-7.8$~pp at W2--W3. The cell-mean recovery ratio is negative
($\rho = -0.66$). The fleet state shifts faster than the lag can
track, and the weights inferred from the previous window do not
generalise to the current window. The pre-registered hypotheses H1
and H3 are rejected; the rejection is reported as the headline
contribution rather than smoothed.

\textbf{Third}, the pre-registered hypothesis that online cannot
exceed the offline-peek ceiling (H2) is also rejected, in the
opposite direction from what was anticipated. At several late-window
cell-window points the lag-1 procedure beats the offline-peek
ceiling by $+1$ to $+3$~pp; the offline strategy appears to overfit
its five-seed calibration sample, and the one-window lag acts as
an implicit regulariser.

The operational summary is conditional: deploy rolling-history online
recalibration only when the per-window distributional change is small
relative to the lag the recalibration window imposes. At high
capacity, the deployment is a net hazard; either keep fixed Paper~4
weights or develop a longer-history calibration procedure --- both
of which are out of this paper's scope.

\textbf{Reproducibility.} The runner, analysis script, pre-registration
protocol, and frozen 1{,}350-row results CSV are available at
\url{https://github.com/Harshavardhanmalla-Labs/research-papers/tree/main/paper7}.

\textbf{Future work.} (i) Multi-window-history EWMA or rolling-mean
calibration to test whether longer-history smoothing reverses the
$K = 200$ hazard; (ii) closed-loop calibration in which the selection
policy is also recalibrated, separating scoring weights from selection
weights; (iii) external validation on real fleet telemetry, where the
fixed Paper~4 weights themselves would be re-fit on real exploitation
event logs before this online-vs-fixed comparison is meaningful.
