Papers~5--8 of the VulnPrio sequence share one internal-validity
threat: every reported P@50 was measured under a trajectory generated
by HygienePrio-full's own top-$K$ selection. Paper~6 reported that
HygienePrio-full's W6 P@50 collapses to $0.062$ at
$K = 200, \lambda = 1$ and attributed the collapse to a mechanism that
exhausts the high-HRS tail --- a mechanism induced, by construction,
by HygienePrio's own selection. This paper isolates the question with
a pre-registered 2-cell, 5-driver, 5-scorer, 25-seed, 6-window
evaluation (7{,}500 rows) filling all five trajectory-driver columns
of the P@50 grid. All three pre-registered hypotheses are rejected,
reframing Papers~5--8. At $K = 200, w = 6$ ($\lambda = 3$),
HygienePrio-full's mean P@50 is $0.075$ on its own trajectory but
$0.70$--$0.72$ under the three independent drivers that do not share
its joint selection signal --- CVSS-only, HRS-only, and Random. The
collapse is not intrinsic: HygienePrio-driven selection exhausts the
joint positive set (EPSS $> 0.10$ $\wedge$ HRS $>$ p75), leaving
$3.8$ surviving positives per $\approx 760$-pair backlog on average
--- a P@50 ceiling of $0.076$ that HygienePrio nearly attains.
EPSS-driven selection also collapses HygienePrio's measured P@50
($0.008$), because it drains the same EPSS-gated positive set.
Per-pair dominance over EPSS-only is $1.000$ under non-draining
drivers at $K = 50$ but $0.393$ under the EPSS-driven trajectory at
$K = 200$; Paper~6's pooled $96\%$ headline (Paper~5's single-cell
figure was 150/150) survives at moderate capacity and under
non-draining drivers. Safe deployment requires a patching queue
driven by a policy that does not drain the EPSS$\wedge$HRS joint
positive set: CVSS-, HRS-, or compliance-driven queues qualify;
EPSS-driven queues do not. All claims are bounded to the synthetic
EEHDA evaluation context.
