\section{Introduction}

Papers~5--8 of the VulnPrio research sequence all bound their findings
to a single trajectory regime --- the one in which HygienePrio-full's
top-$K$ selection drives fleet evolution at every window. The choice was
deliberate and pre-registered: when each method drives its own
counterfactual trajectory, the resulting per-method residual backlogs
differ, the per-window positive sets are computed against different
states, and direct cross-method P@50 comparisons become
non-identifiable. The HygienePrio-driven trajectory was the
identifiability-preserving compromise.

Paper~6~\cite{paper6capacity} additionally reported that HygienePrio-full's
W6 P@50 collapses at $K \in \{100, 200\}$ on this baseline trajectory and
reported that the mechanism exhausts the high-HRS tail: HygienePrio-full
preferentially remediates high-HRS hosts, those hosts exit the upper
HRS tail, and HygienePrio's discriminative signal degrades. The
mechanism is, by construction, induced by HygienePrio's own selection.

This paper asks the inevitable follow-up. \textit{If the collapse is
induced by HygienePrio's selection draining the HRS tail, what happens
when a different method drives the trajectory?} A capacity-$K = 200$
deployment that uses HygienePrio for scoring but, say, CVSS-only for
selection (or vice versa) does not exhibit the recursive
HRS-tail-exhaustion mechanism. The Paper~6 collapse should not appear.

We pre-registered three hypotheses
(\texttt{paper9/design/PAPER9\_PROTOCOL.md}, locked 2026-06-05 before
any self-trajectory result was inspected) and ran a 7{,}500-row
evaluation that fills in all five trajectory-driver columns of the
P@50 grid at $K \in \{50, 200\}$, $\lambda = 3$. The results retroactively
reframe Papers~5--8.

Throughout the paper we call CVSS-only, HRS-only, and Random the
\emph{non-draining drivers}: their selection does not preferentially
drain the EPSS $> 0.10$ $\wedge$ HRS $>$ p75 joint positive set that
defines the ground truth. HygienePrio-driven and EPSS-driven selection
both drain that set, each through its EPSS-gated component.

\subsection{Contributions}

\begin{itemize}
\item \textbf{C1 --- Trajectory grid.} The first pre-registered
trajectory-stratified evaluation of HygienePrio: 5 driver methods
$\times$ 5 scoring methods $\times$ 2 cells $\times$ 25 seeds
$\times$ 6 windows = 7{,}500 rows.

\item \textbf{C2 --- The collapse is selection-induced.} Paper~6's
W6 P@50 collapse of HygienePrio-full from $\sim 0.5$ at $K = 50$ to
$0.062$--$0.075$ at $K = 200$ is reproduced under the
HygienePrio-driven trajectory. Under the independent drivers that do
not share HygienePrio's joint selection signal --- CVSS-only,
HRS-only, and Random --- HygienePrio's W6 P@50 at $K = 200$ sits
between $0.70$ and $0.72$. EPSS-driven selection also collapses
HygienePrio's measured P@50 ($0.008$), because it drains the same
EPSS-gated positive set. The collapse mechanism is recursive, not
intrinsic.

\item \textbf{C3 --- Both collapses are positive-set exhaustion.} At
$K = 200$ under the EPSS-only-driven trajectory, every scorer's W6
P@50 collapses to $0.001$--$0.012$: EPSS-only's selection so
aggressively remediates the high-EPSS tail that the binary
ground-truth positive set is itself exhausted by W6. The
HygienePrio-driven collapse is the \emph{same} mechanism: at
$K = 200$, W6 under $T_{\mathrm{HP}}$ the joint positive set holds a
mean of only $3.8$ pairs (of $\approx 760$), a P@50 ceiling of
$0.076$ that HygienePrio nearly attains ($0.075$) while Random scores
$0.004$. HygienePrio's signal has not degraded --- the positives it
is scored against have been patched away.

\item \textbf{C4 --- Per-pair dominance is trajectory-conditional.}
At $K = 50$, HygienePrio-full $>$ EPSS-only on $100\%$ of (seed,
window) pairs under every driver. At $K = 200$ under
EPSS-only's own driver, the fraction collapses to $0.393$
(where both methods are near zero together). At $K = 200$ under
HRS-only, CVSS-only, or Random drivers, the fraction is $1.000$.
Paper~6's pooled $96\%$ headline statistic (Paper~5's own
single-cell figure was 150/150) is preserved at moderate
capacity and under non-draining drivers; it does not survive at the
EPSS-self-driven high-capacity corner.

\item \textbf{C5 --- Sharpened operational reading.} HygienePrio's
absolute floor at high capacity is intact whenever the patching
queue is driven by a policy that does not drain the
EPSS$\wedge$HRS joint positive set --- CVSS-, HRS-, or
compliance-driven queues qualify; HygienePrio-driven and
EPSS-driven queues do not. The Paper~6 H4 collapse is a property of
positive-set-draining deployment, not of hygiene-augmented scoring
as a method. A team using HygienePrio for scoring should expect
the high absolute P@50 reported in Paper~5--7 across capacity
regimes, provided a non-draining policy drives the patching queue.
\end{itemize}

\subsection{Relationship to Prior Papers}

This paper is the ninth in the VulnPrio sequence. Papers~5--8
identified a number of regime-specific findings (temporal stability,
capacity-induced collapse, deployable calibration, smoothing
falsification); the present paper shows that the most prominent of
those findings --- Paper~6's H4 high-capacity collapse --- is partly
a closed-loop artefact. The other findings (Paper~5 per-pair dominance,
Paper~7's lag-1 calibration in moderate-$K$, Paper~8's smoothing
penalty) are unchanged but should be cited together with the
trajectory column they were measured on.
