\section{Methodology}

\subsection{Scorers (Inherited)}

All five scorers are inherited verbatim from Paper~4~\cite{paper4hygieneprio}
with the fixed Paper~4 calibrated weights:
\begin{equation}
\begin{aligned}
S_{\mathrm{HP}}(h,c) =\;& 0.7\,\mathrm{EPSS}(c) + 0.5\,\mathrm{HRS}(h) \\
                       & + 0.1\,\mathrm{KEV\_recency}(c) \\
                       & + 0.2\,\bigl(\mathrm{EPSS}(c) \cdot \mathrm{HRS}(h)\bigr).
\end{aligned}
\end{equation}
Baselines are EPSS-only ($S = \mathrm{EPSS}(c)$), HRS-only ($S = \mathrm{HRS}(h)$),
CVSS-only ($S = \mathrm{CVSS}_{\mathrm{base}}(c)$), and Random
(seed-deterministic uniform ranking). We deliberately use Paper~4
fixed weights and not Paper~7/8 online recalibration: the question
in this paper is about \textit{trajectory effects} under a held-constant
scorer, not about calibration.

\subsection{Driver-Stratified Fleet Evolution}

For each (cell $K$, driver $m_{\text{drive}}$, seed $s$):
\begin{enumerate}
\item Initialise fleet from EEHDA generator at seed $s$.
\item For each window $w = 1, \ldots, 6$:
\begin{enumerate}
\item Compute $(\text{pairs}_w, \text{HRS}_w)$ from current state;
label per the per-window ground truth definition.
\item For each scoring method $m_{\text{score}} \in \mathcal{M}$:
rank pairs, compute P@50, record one row.
\item If $w < 6$: select $m_{\text{drive}}$'s top-$K$ pairs, apply
remediation, disclose Poisson$(\lambda)$ new CVEs, random-walk EPSS,
update telemetry. (Step uses RNG seeded by $(s, w)$ for reproducibility.)
\end{enumerate}
\end{enumerate}

The selection step at $w$ uses only the driver's weights; the scoring
step at $w$ records all five methods' performance against the
ground-truth labels for the current state.

\subsection{Trajectory Effect Quantification}

For each scoring method $m$, the per-cell W6 trajectory effect is
\begin{equation}
\Delta^{\mathrm{traj}}_m(K) = \max_{m'} \mathrm{P@50}^m_{w=6, K}(T_{m'})
                          - \min_{m'} \mathrm{P@50}^m_{w=6, K}(T_{m'}).
\end{equation}
A large $\Delta^{\mathrm{traj}}_m$ means method $m$'s W6 performance
depends substantially on which method drives the trajectory; a small
$\Delta^{\mathrm{traj}}_m$ means $m$'s performance is intrinsic.

\subsection{Per-Pair Dominance Under Counterfactual Trajectory}

For each (cell, driver), the per-pair dominance of HP-full over EPSS-only
is
$\Pr[\mathrm{P@50}^{\mathrm{HP}}_{s, w} > \mathrm{P@50}^{\mathrm{EPSS}}_{s, w} \mid
T_{m_{\mathrm{drive}}}, K]$,
computed over the 150 (seed, window) pairs. Paper~6 reported this
fraction was 0.960 on the HP-driven trajectory, pooled over its full
20-cell $(K, \lambda)$ grid, with a per-cell range of
76.7\%--100\%; the present paper tests whether the fraction survives
on the EPSS-only trajectory.
