\section{Discussion}
\label{sec:discussion}

\subsection{What This Paper Changes About Paper~6}

Paper~6~\cite{paper6capacity} reported HygienePrio's H4 absolute-floor
collapse at $K \in \{100, 200\}$ as a property of hygiene-augmented
scoring under high capacity. The present paper shows the collapse is
substantially a property of \textit{positive-set-draining deployment}:
when the queue-driving policy preferentially remediates the
EPSS$\wedge$HRS joint positive set, that set exhausts, and every
scorer aligned with it is capped by the surviving positive mass
(\S\ref{sec:results}: $3.8$ mean positives, ceiling $0.076$).
Under the non-draining drivers --- CVSS-only, HRS-only, and the
trivial Random baseline --- HygienePrio's W6 mean P@50 at K=200 lands
at $0.701$--$0.713$, an order of magnitude above the self-trajectory
number. EPSS-driven selection, by contrast, also collapses
HygienePrio's measured P@50 ($0.008$) because it drains the same
EPSS-gated positive set.

The operational corollary is sharp. A team that uses HygienePrio for
scoring and lets some \textit{other} policy --- for example, a
ticketing system, a compliance-driven schedule, or a CVSS-based
queue --- determine which pairs are actually patched first will not
experience the Paper~6 collapse. The collapse is a closed-loop
artefact, not a property of hygiene-augmented scoring as a method.

\subsection{Why EPSS-Self-Driven Destroys Everything}

The K=200, $T_{\mathrm{EPSS}}$ column of Table~\ref{tab:w6grid} contains
the most extreme cell in the grid. Five W6 P@50 values, all in
$[0.000, 0.012]$. The mechanism is ground-truth-set exhaustion:
EPSS-only's selection at K=200 removes the high-EPSS tail so fast that
the binary positive condition (EPSS $> 0.10$) is satisfied by an
essentially empty residual backlog. Once the positive set is empty,
P@50 is mechanically zero regardless of which scorer is being
evaluated --- you cannot rank a non-existent positive.

This is the same mechanism that produces the HP-driven collapse, taken
to its extreme. Both HygienePrio-driven and EPSS-driven selection
drain the EPSS-gated joint positive set; EPSS-only drains it deeper
(mean $0.6$ surviving positives versus $3.8$ under
$T_{\mathrm{HP}}$), reaching a literal zero floor. Both are
positive-set-exhaustion artefacts of the evaluation; neither is an
intrinsic scoring failure.

\subsection{What Paper~6's 96\% Per-Pair Dominance Actually Means}

Paper~6 reported that HygienePrio-full $>$ EPSS-only at P@50 in
$96.0\%$ of (cell, seed, window) triples ($2{,}881/3{,}000$, pooled
over its 20-cell grid) under the (then-implicit) HygienePrio-driven
trajectory (Paper~5's own single-cell figure was 150/150). The
present paper finds that this
statistic survives at $K = 50$ under every driver (always $1.000$),
survives at $K = 200$ under HRS, CVSS, and Random drivers
($1.000$), partially survives at $K = 200$ under HygienePrio's own
driver ($0.800$), and \textit{does not} survive at $K = 200$ under
the EPSS-only driver ($0.393$). The interpretation: per-pair
dominance is a robust property of HygienePrio under any
non-draining selection, including the natural baselines an operations
team would deploy if not using HygienePrio's score for selection.
Under the EPSS-self-driven regime both methods collapse together,
and the comparison becomes degenerate.

\subsection{What Paper~6's H4 Rejection Means After This Paper}

Paper~6's H4 rejection now reads as follows. HygienePrio-full's
absolute W6 P@50 at $K \geq 100$ is degraded only when the
trajectory is driven by a policy that drains the EPSS$\wedge$HRS
joint positive set (HygienePrio itself, or EPSS-only). The mechanism
is joint-positive-set exhaustion. On any non-draining driver, the
absolute floor is
intact at the Paper~5 level ($\sim 0.5$ or higher). The original
H4 hypothesis ``HygienePrio retains $\geq 0.4$ at every cell'' is
\textit{re-supportable} under the qualified statement ``on every cell,
on at least one non-draining driver''. We do not formally re-test Paper~6
H4 here because doing so would constitute hypothesising after results
known (HARKing); we report the observation honestly and leave a
new pre-registered H4-style restatement to future work.

\subsection{Why the Trajectory Effect is Asymmetric Across Scorers}

The trajectory-effect range $\Delta^{\mathrm{traj}}_m$ is largest for
HP-full and EPSS-only and smallest for CVSS-only and Random. The
asymmetry has a clean structural interpretation: a scorer's W6
performance depends on whether the driver preferentially drained the
ground-truth positive set that the scorer's ranking is aligned with.
HP-full and EPSS-only rank the EPSS-gated joint positive set highest,
so the HP-driven and EPSS-driven trajectories --- both of which drain
that set --- collapse their measured precision. CVSS-only relies on
the CVSS upper tail (which is not part of the ground-truth condition)
so no driver in the grid preferentially starves it. Random relies on
no signal. The two scorers most sensitive to trajectory are the two
scorers whose ranking is most aligned with the ground-truth positive
set --- which is the same property that makes them the strongest
scorers in the first place.

\subsection{Operational Recommendations}

Sharpened from Papers~5--8:
\begin{itemize}
\item Use HygienePrio for scoring across all studied capacity
regimes; its per-pair dominance over EPSS-only is preserved
whenever the patching queue is driven by a policy that does not
drain the EPSS$\wedge$HRS joint positive set. CVSS-, HRS-, or
compliance-driven queues qualify; HygienePrio-driven and
EPSS-driven queues at high capacity do not.
\item Do not let HygienePrio be both the scorer and the queue-driving
policy at $K \geq 100$. Either (i) decouple --- use HygienePrio
for ranking but let another policy (ticketing system, CVSS queue,
human triage) drive the patching cycle, or (ii) accept the Paper~6
H4-style collapse as the cost of full automation.
\item Do not deploy EPSS-only as both scorer and selection policy at
high capacity. EPSS-self-driven at K=200 produces a literal zero
floor by W6.
\end{itemize}

\subsection{Relationship to the Research Sequence}

This paper closes a gap that Papers~5--8 explicitly bounded but did
not measure. The cumulative arc is unchanged in spirit: hygiene
augmentation helps prioritization. But the headline ``HygienePrio
holds up across regimes'' is now sharper. It holds up across regimes
\textit{except} when fleet evolution at high capacity is driven by a
positive-set-draining policy --- HygienePrio itself, or EPSS-only.
That last condition is operationally
controllable, and the recommendation is to control it.
