\section{Threats to Validity}
\label{sec:threats}

The threats taxonomy follows Wohlin et al.~\cite{wohlin2012experimentation}.

\textbf{Conclusion validity.} The 7{,}500-row evaluation supports
$\sim 50$-row cell-means per (K, driver, scorer, window) --- a
reasonably tight estimator. Bootstrap CIs (10{,}000 resamples) at
the W6 cells separate the HP-driven HP value ($0.075$) from the
CVSS/HRS/Random-driven HP values ($0.701$--$0.713$) without overlap.
The qualitative finding does not depend on the CI width.

\textbf{Internal validity.}

\textit{(i) Per-window ground truth re-uses HRS percentiles.} The
binary positive condition incorporates HRS $>$ 75th percentile
recomputed each window. Under HP-driven and HRS-driven trajectories,
the recomputed percentile threshold moves substantially each window;
under CVSS-driven and Random-driven trajectories, it moves less.
This means the ``HP scored on T\_CVSS'' cell is operating against a
relatively stable positive set whose composition is similar to W1,
while the ``HP scored on T\_HP'' cell is operating against a
fast-moving positive set. The non-identifiability is unavoidable
under the per-window threshold convention; we report it transparently
and bound claims to that convention.

\textit{(ii) The EPSS-self-driven collapse is partly a structural
artefact.} When EPSS-only's selection drives evolution at K=200,
nearly all CVEs with EPSS $> 0.10$ are remediated by W3--W4, and the
ground-truth positive condition $EPSS > 0.10$ becomes near-empty.
The literal zero W6 P@50 values reflect an essentially empty positive
set, not a scoring failure. We report this honestly; the qualitative
finding (``EPSS-self-driven is the deepest sink'') is robust but
should not be read as ``EPSS-only is the worst scorer''.

\textit{(iii) Two cells only.} K=50 and K=200 anchor low and
collapse regimes; K=100 and K=150 cells are interpolations not
measured here. The Paper~6 H4 dataset can be used by readers to
fill in the K=100 cell under HP-driven trajectory.

\textbf{Construct validity.} P@50 with binary relevance, recomputed-per-window
HRS-percentile ground truth, and fixed Paper~4 scorer weights are
inherited from Papers~5--8. We deliberately do not vary calibration
strategy (the Papers~7--8 axis) because doing so would interact with
the trajectory question; isolating one effect at a time is a
methodological choice that the protocol locks.

\textbf{External validity.} Inherited from Papers~4--8: synthetic
EEHDA structural priors, 14-day window, 0.15 patch debt reduction,
0.02 EPSS random walk, 8\% KEV prevalence. The qualitative finding ---
that recursive-deployment collapse is selection-induced --- is more
robust than any specific number; the specific W6 levels ($0.075$ vs
$0.701$) are distributional. External validation on real fleet
telemetry with longitudinal exploitation outcomes is the appropriate
next step.
