\section{Related Work}

\textbf{Trajectory-coupling threat in Papers~5--8.}
Paper~5~\cite{paper5temporal}~§9, Paper~6~\cite{paper6capacity}~§9,
Paper~7~\cite{paper7online}~§9, and Paper~8~\cite{paper8multi}~§9 all
acknowledge the HygienePrio-driven trajectory as an internal-validity
threat. Each cited a ``fully factorial each-method-drives-its-own''
future-work item as the appropriate counterfactual. The present paper
implements that counterfactual in a pre-registered form.

\textbf{High-capacity collapse in Paper~6.} Paper~6 reported
HygienePrio-full's W6 P@50 collapse at $K \in \{100, 200\}$ and
attributed it to high-HRS-tail exhaustion. The present paper retains
the collapse statistic on the HP-driven trajectory but shows it
disappears under HRS-blind drivers, revising the interpretation from
``intrinsic property of hygiene-augmented scoring at high capacity''
to ``closed-loop artefact of recursive deployment''.

\textbf{EPSS dynamics.} Jacobs et al.~\cite{jacobs2021epss,jacobs2020improving}
established per-CVE exploit-prediction scoring. Ravalico
et al.~\cite{ravalico2025epsstemporal} studied per-CVE EPSS score drift.
The present paper documents a distinct effect: \textit{EPSS-as-policy}
remediation at high capacity exhausts the ground-truth positive set
within six windows on the simulated fleet, producing a literal zero
floor for every scorer evaluated against that trajectory. Neither prior
study addressed the policy-level effect.

\textbf{Counterfactual evaluation in security ML.} The general pattern
--- evaluating method A on the data trajectory that method B would
have generated --- appears in counterfactual learning to rank and
off-policy evaluation. The instance studied here is the simplest
form: a deterministic policy generates the trajectory, and the
counterfactual is computed by re-running the simulation under each
candidate policy. We do not survey the broader counterfactual-policy
literature; the question this paper resolves is operationally specific
to the Paper~6 H4 claim.

\textbf{Cyber-hygiene benchmarking.} HygieneBench~\cite{paper3hygienebench},
HygienePrio~\cite{paper4hygieneprio}, the temporal extension~\cite{paper5temporal},
capacity sweep~\cite{paper6capacity}, online calibration~\cite{paper7online},
and multi-history calibration~\cite{paper8multi} together constitute
the methodological substrate within which this paper sits.

\textbf{Policy mandates.}
CISA BOD 22-01~\cite{cisa2021bod2201} and 23-01~\cite{cisa2022bod2301}
along with NIST SP 800-40 Rev.~4~\cite{nist2022sp80040r4} define the
operational scheduling regime under which any vulnerability-prioritization
deployment must operate. The recommendation that scoring and selection
should be decoupled at high capacity follows from this paper's
findings and aligns with the spirit of the BOD mandates' separation of
discovery, prioritisation, and remediation roles.
