\section{Conclusion}
\label{sec:conclusion}

A pre-registered 7{,}500-row self-trajectory evaluation of the five
HygienePrio-family prioritization methods at $K \in \{50, 200\}$,
$\lambda = 3$, $W = 6$, on the 25 evaluation seeds inherited from
Papers~5--8, produces three findings that retroactively reframe the
research sequence.

\textbf{First}, Paper~6's headline ``HygienePrio collapses at high
capacity'' is rejected as an intrinsic property of hygiene-augmented
scoring. At $K = 200, w = 6$, HygienePrio-full's mean P@50 is $0.075$
on its own trajectory but $0.701$ on CVSS-driven, $0.713$ on
HRS-driven, and $0.706$ on Random-driven trajectories. The collapse
is a positive-set-exhaustion artefact: HygienePrio's own selection
patches away the EPSS$\wedge$HRS joint positive set, leaving a mean
of $3.8$ positives per backlog --- a P@50 ceiling of $0.076$ that
HygienePrio's still-intact signal nearly attains ($0.075$, versus
Random's $0.004$).

\textbf{Second}, EPSS-only's selection at $K = 200$ produces a literal
zero W6 P@50 for every scorer (range $0.001$--$0.012$). The
ground-truth positive set is structurally exhausted by EPSS-only's
aggressive remediation of the high-EPSS tail. EPSS-self-driven at
high capacity is the deepest sink in the studied grid.

\textbf{Third}, HygienePrio's per-pair dominance over EPSS-only is
trajectory-conditional. At K=50 it is $1.000$ under every driver;
at K=200 it is $1.000$ under HRS, CVSS, and Random drivers, $0.800$
under HP's own driver, and $0.393$ under EPSS-only's driver
(where both methods collapse together). Paper~6's pooled $96\%$
headline statistic (Paper~5's own single-cell figure was 150/150) is
preserved at moderate capacity and under non-draining
drivers --- the regimes most relevant to actual deployment.

The operational reading is sharper than Papers~5--8 allowed:
HygienePrio is a strict improvement over EPSS-only across the
studied regimes whenever the patching queue is driven by a policy
that does not drain the EPSS$\wedge$HRS joint positive set. CVSS-,
HRS-, or compliance-driven queues qualify; HygienePrio-driven and
EPSS-driven queues at high capacity do not (HygienePrio's dominance
falls to $0.393$, and its measured floor to $0.008$, under
$T_{\mathrm{EPSS}}$ at $K = 200$). The Paper~6 H4 collapse is a known
closed-loop hazard, not a property of the scoring method itself, and
is operationally controllable by driving the queue with a
non-draining policy.

\textbf{Reproducibility.} The runner, analysis script, pre-registration
protocol, and frozen 7{,}500-row results CSV are available at
\url{https://github.com/Harshavardhanmalla-Labs/research-papers/tree/main/paper9}.

\textbf{Future work.}
\textit{(i)} A pre-registered re-test of Paper~6's H4 hypothesis under
the qualified statement ``on every cell, on at least one non-draining
driver''. Doing this rigorously requires a fresh seed set to avoid
HARKing on the present data.
\textit{(ii)} Trajectory effects on calibration: do Paper~7's lag-1
recovery ratio and Paper~8's smoothing penalty change under non-HP
drivers? Both papers measured under T\_HP only.
\textit{(iii)} External validation on real fleet telemetry with
longitudinal exploitation outcome data.
\textit{(iv)} A cross-trajectory evaluation in which the scorer
\textit{also} predicts the next-window driver, modelling a fully
adaptive closed-loop policy rather than two static ones.
