% Auto-converted from paper2_full_draft.md §10.
% Wording preserved; no claims added.
\section{Metrics and Inference Policy}
The pre-registered primary metric is \texttt{ehd\_absolute} (Exposure-Host-Day), reported as paired-seed ΔEHD relative to \texttt{epss\_only} at the central cell. Secondary metrics are \texttt{eehda\_relative}, \texttt{fraction\_of\_oracle} (reported descriptively; oracle inference is disabled by pre-registration), \texttt{scheduler\_feasibility\_rate}, and \texttt{capacity\_efficiency}. Precision, recall, nDCG at $K$, and KEV-deadline-breach rate are diagnostic-only due to label sparsity; these never enter a headline claim.

The pre-registered inference policy sets the meaningful-effect threshold at 5,000 host-days (chosen above the per-seed paired-$\Delta$ noise floor reported in~\cite{Malla2026VulnPrio} of 2,331--3,673\,hd) and computes the MDE at $n = 30$ paired seeds, $\alpha = 0.05$, power $= 0.80$, two-sided (MDE-d $= 0.5292$). Under $\times 1.0$ to $\times 1.5$ sparsity inflation the MDE in host-days sits in 1,234--2,916\,hd, below the 5,000-hd meaningful threshold.

Five Holm correction families are pre-registered. Degenerate-difference comparisons are auto-dropped (\texttt{kev\_first $-$ epss\_only} was identically zero under the companion fixtures of~\cite{Malla2026VulnPrio} and is dropped if degeneracy is reproduced). Oracle inference is disabled. A descriptive-language guardrail applies whenever a Holm rejection falls inside $\pm$5,000 host-days. Significance phrasing is forbidden for diagnostic-only metrics.
