% Auto-converted from paper2_full_draft.md §12.
% Wording preserved; no claims added.
\section{Discussion}
Sparse public-feed labels are a methodological constraint, not a flaw in any particular model. The gate methodology is intended to surface that constraint before per-feature calibration is attempted, rather than discover it after weights have been fitted and presented. Treating the host-CVE record total as if it were the calibration unit is a misleading habit: the calibration unit is the CVE, and a few thousand records that share a handful of CVE-level labels do not provide more calibration information than the CVE count alone.

The sensitivity sweeps add reproducibility evidence and a set of axis-level descriptive observations: at the cell-mean level the priors do separate from each other, but at the seed level the per-cell variance is the same order of magnitude as the between-cells variance — the within-cell variance criterion fires on every axis. This is a useful signal in itself: it cautions against treating seed-aggregated mean EHD differences as decision evidence at this seed budget. A higher seed budget (deferred $n = 50$ and $n = 100$ runs) would allow this criterion to be re-evaluated.

The work says nothing about EPSS in general; the released v3-era EPSS is used as one feature among several, without retraining or critique. The work says nothing about whether KEV is an adequate ground-truth label in general; it is a sparse signal on the catalog $\times$ era examined. The work says nothing about CVSS quality. The work does not claim that context-aware priors are meaningfully better than EPSS for prioritization; descriptive observations that some priors produce lower EHD at the central cell are reported, and the sensitivity sweeps fall in the descriptive-only zone under the variance criterion.

We do not claim production-readiness. We do not claim deployment evidence. We do not claim government use. We do not claim compliance achievement.

The negative feasibility finding is useful precisely because it is honest and small. It is a data point about a specific catalog × era × label choice. It does not generalise without further measurement, and we do not attempt that generalisation here.
