\section{Threats to Validity}
\label{sec:threats}

\textbf{Conclusion validity.} The Spearman correlations underlying
H1, H2, and H4 are computed on five $\tau$ values. The small sample
limits statistical power, and the pre-registered $|\rho| \geq 0.8$
threshold is met or missed by point estimates rather than strong
inferential claims. We report the per-$\tau$ point values directly
to enable independent assessment.

\textbf{Internal validity.}

\textit{(i) $\tau$ grid is finite and pre-registered.} The H3
``operating point exists'' claim is bounded to the five $\tau$ values
in the grid. A denser grid could expose an operating point that the
sparse grid misses, but the protocol locked the grid before any
result was inspected and we do not augment it post hoc.

\textit{(ii) Selection-policy coupling.} As in Papers~7--10, the
fleet trajectory is driven by HygienePrio-full under \textsf{fixed}
weights. All strategies share this trajectory; the adaptive
procedure does not co-evolve the selection policy with its own
weights. Paper~9~\cite{paper9selftraj} addressed the cross-method
trajectory question; the present paper inherits the fixed-trajectory
convention and bounds claims accordingly.

\textit{(iii) Detector simplicity inherited from Paper~10.} The
one-threshold magnitude test is the simplest detector; richer
detectors (CUSUM, Bayesian) might produce different Pareto curves
that this sweep cannot characterise.

\textbf{Construct validity.} ``Worst per-window delta'' uses the
minimum over $w \in \{2, \ldots, 6\}$ of the cell-mean. At high
capacity the W2 window typically has the largest pure-fixed/pure-lag1
spread and dominates the worst-delta statistic; this is intentional
because W2 is the first window where the detector is operational.

\textbf{External validity.} The $\tau$ grid is calibrated to the
synthetic regime studied. A real fleet's per-window calibration-target
shift distribution would re-locate the Pareto curve along the
$\tau$ axis. The qualitative finding --- whether the Pareto curve
contains an operating point that satisfies both Paper~10 tolerances ---
is more robust than the specific $\tau^\star$ value (if any).
