\section{Introduction}

Single-cell evaluations of vulnerability prioritization methods report
performance at one operating point: one remediation capacity, one CVE
arrival rate, one window cadence. Paper~5~\cite{paper5temporal} extended
single-window evaluation~\cite{paper4hygieneprio} to six rolling windows
at a fixed cell ($K = 50, \lambda = 3$) and showed that EPSS-only
Precision@50 decays from $0.331$ to $0.034$ as the high-EPSS tail of
the backlog is exhausted by capacity-constrained remediation. That study
left two operational questions unresolved:

\textbf{Q1.} How does decay depend on capacity $K$? Faster remediation
should drain the high-EPSS tail faster --- but does the relationship
scale monotonically?

\textbf{Q2.} How does new-CVE arrival rate $\lambda$ replenish the high-EPSS
tail? Above some critical $\lambda$, decay should slow or stall.

Both matter operationally: an organisation with $K = 200, \lambda = 12$
sits in a very different regime from one with $K = 25, \lambda = 1$, and
Paper~5's single-cell result cannot tell either organisation what to expect.

This paper sweeps a pre-registered 5$\times$4 grid of $(K, \lambda)$
on the 25 evaluation seeds inherited from Paper~5, generating 15{,}000
result rows under the same EEHDA fleet model. We report three
findings honestly against the pre-registration.

\subsection{Contributions}

\begin{itemize}
\item \textbf{C1 --- Two-dimensional capacity-arrival sweep.} A
pre-registered grid of 20 $(K, \lambda)$ cells on the EEHDA fleet,
extending Paper~5's single-cell simulator with explicit cell-level
control of capacity and Poisson arrival rate; 15{,}000 frozen result rows.

\item \textbf{C2 --- Universal EPSS decay across the grid.} EPSS-only
decay slope is strictly negative in all 20 cells (range $-0.025$ to
$-0.052$ P@50/window). The pre-registered ratio hypothesis H3 fails to
identify a steady-state cell within the grid; we report this descriptively
rather than as a binary claim.

\item \textbf{C3 --- Predicted monotonicity rejected.} Spearman
correlations for the predicted monotone scaling of EPSS decay with $K$
(H1) and $\lambda$ (H2) fall below the pre-registered $|\rho| \geq 0.8$
threshold across most slices. The underlying compositional dynamics
are non-monotone in the synthetic regime studied; we report the
non-monotonicities directly rather than smoothing them.

\item \textbf{C4 --- HygienePrio also collapses at high capacity
under self-driven (closed-loop) selection.}
The pre-registered claim that HygienePrio-full retains W6 P@50
$\geq 0.40$ across all cells (H4) is \textit{rejected}. At $K = 200$,
HygienePrio-full falls to a W6 mean of $0.062$ ($\lambda = 1$). The
mechanism is symmetric to EPSS-only's collapse: high-throughput
remediation under self-driven selection exhausts the high-HRS tail,
after which the hygiene signal carries little additional information.
Paper~9~\cite{paper9selftraj} shows the collapse is specific to
self-driven selection and does not occur under independent drivers.

\item \textbf{C5 --- Per-pair dominance survives.} HygienePrio-full
outperforms EPSS-only at P@50 in $96.0\%$ of all (cell, seed, window)
triples ($2{,}881$/$3{,}000$). Minimum per-cell dominance is $76.7\%$.
Hygiene augmentation is a strict improvement over EPSS-only in the
regimes studied, but is not a guarantee of absolute scheduling quality
at the high-capacity end.
\end{itemize}

\subsection{Relationship to Prior Papers}

This paper is the sixth in the VulnPrio research sequence. Paper~1~\cite{paper1vulnprio}
reported a null result for CVE-level augmentation at one window.
Paper~3~\cite{paper3hygienebench} demonstrated discriminative structure
in hygiene signals. Paper~4~\cite{paper4hygieneprio} integrated those
signals into the HygienePrio scorer and showed $\approx 31$~pp Precision@50
improvement over EPSS-only at one window. Paper~5~\cite{paper5temporal}
showed the gap is robust across six windows at one cell. The present
paper sweeps the cell-defining parameters and finds that the absolute
P@50 of \textit{both} methods is regime-dependent, with HygienePrio's
absolute floor failing at high capacity --- while its relative
advantage over EPSS-only is preserved across the grid.
