\section{Problem Formulation}
\label{sec:problem}

\subsection{Sweep Setting}

We extend the prior temporal-stability evaluation's~\cite{paper5temporal} single-cell multi-window simulation
to a two-dimensional sweep over remediation capacity $K$ and Poisson
arrival rate $\lambda$. Let $F_w$ denote the fleet state at window $w \in
\{1, \ldots, W\}$ with $W = 6$. For each cell $(K, \lambda)$ in the grid,
each window executes:

\begin{enumerate}
\item \textbf{Score.} Compute $S_w(h, c)$ for all unpatched applicable
pairs $(h, c) \in V_w$ using $F_w$.
\item \textbf{Select.} Rank pairs descending; the top-$K$ action set
$A_w$ is selected by HygienePrio-full (used as the policy that drives
fleet evolution for \textit{all} methods scored at this window).
\item \textbf{Remediate.} Mark pairs in $A_w$ patched; reduce host
patch debt and recover telemetry freshness for acted hosts.
\item \textbf{Disclose.} Draw $n \sim \mathrm{Poisson}(\lambda)$ new
(host, CVE) rows with EPSS, CVSS, and KEV attributes sampled from the
HygienePrio~\cite{paper4hygieneprio} fixture distributions.
\item \textbf{Update.} Random-walk perturb EPSS scores ($\sigma = 0.02$);
accumulate telemetry staleness for non-acted hosts.
\item \textbf{Advance.} $F_{w+1} \leftarrow$ updated state.
\end{enumerate}

\subsection{Ground Truth (per Window)}

Following~\cite{paper5temporal}: $(h, c)$ is a positive at
window $w$ if $\mathrm{EPSS}(c) > 0.10$, $\mathrm{HRS}(h)$ exceeds the
fleet's 75th percentile at $w$, and $(h, c) \in V_w$. The HRS-percentile
threshold is recomputed per window; this structural choice, adopted
from~\cite{paper5temporal} for comparability, is restated as a threat
in \S\ref{sec:threats}.

\subsection{Metrics}

\begin{itemize}
\item \textbf{P@$K'$} (primary), with $K' \in \{50, 100, 250\}$
metric levels reported per cell, per window, per seed. Note that $K'$
is the metric-evaluation level, separate from the cell's capacity $K$
that controls fleet evolution.
\item \textbf{Decay slope.} OLS slope of P@50 versus window index
($w = 1, \ldots, 6$), per (cell, seed, method).
\item \textbf{W6 retention.} Cell-mean P@50 at $w = 6$ per method.
\end{itemize}

\subsection{Pre-Registered Hypotheses}

\begin{description}
\item[H1] EPSS-only mean decay slope is monotonically more negative as
$K$ increases at every fixed $\lambda$ (Spearman $\rho \leq -0.8$).
\item[H2] EPSS-only decay slope is monotonically less negative (closer
to zero) as $\lambda$ increases at every fixed $K$ (Spearman $\rho \geq +0.8$).
\item[H3] A critical ratio $K/\lambda$ exists at which the EPSS-only
slope $\geq -0.01$ P@50/window (descriptive; no binary test).
\item[H4] HygienePrio-full retains W6 mean P@50 $\geq 0.40$ across all
20 cells.
\end{description}

The full pre-registration protocol, including hypotheses, decision
rules, and stop rules, accompanies the reproducibility artifact release.
