\section{Methodology}

\subsection{Scorers}

All five scorers are inherited verbatim from HygienePrio~\cite{paper4hygieneprio}
and the prior temporal-stability evaluation~\cite{paper5temporal} with fixed calibrated weights:
\begin{equation}
\begin{aligned}
S_{\mathrm{HP}}(h,c) =\;& 0.7\,\mathrm{EPSS}(c) + 0.5\,\mathrm{HRS}(h) \\
                       & + 0.1\,\mathrm{KEV\_recency}(c) \\
                       & + 0.2\,\bigl(\mathrm{EPSS}(c) \cdot \mathrm{HRS}(h)\bigr),
\end{aligned}
\label{eq:hp}
\end{equation}
\begin{equation}
\begin{aligned}
\mathrm{HRS}(h) =\;& 0.50\,\mathrm{PatchPosture}(h) \\
                  & + 0.30\,\mathrm{ADExposure}(h) \\
                  & + 0.20\,\mathrm{TelFresh}(h).
\end{aligned}
\end{equation}
Baselines are EPSS-only ($S = \mathrm{EPSS}(c)$), HRS-only
($S = \mathrm{HRS}(h)$), CVSS-only ($S = \mathrm{CVSS}_{\mathrm{base}}(c)$~\cite{first2019cvss}),
and Random (seed-deterministic uniform ranking).

\subsection{Fleet-State Evolution}

The window-$w$ fleet $F_w$ is advanced to $F_{w+1}$ in four steps:
\begin{enumerate}
\item \textbf{Remediate.} The top-$K$ pairs selected by HygienePrio-full
are marked patched. PatchPosture is recomputed.
\item \textbf{Disclose.} Draw $n_w \sim \mathrm{Poisson}(\lambda)$ new
(host, CVE) rows. Each row is attached to a random host drawn uniformly
from the fleet, with EPSS, CVSS, and KEV attributes sampled from the
HygienePrio~\cite{paper4hygieneprio} fixture distributions.
\item \textbf{EPSS update.} Apply $\mathcal{N}(0, 0.02^2)$ random-walk
perturbation to EPSS scores of all surviving unpatched pairs; clip to
$[10^{-4}, 1]$.
\item \textbf{Telemetry update.} For acted hosts, decrement staleness
days by $9.0$ (recovery $-0.30$). For non-acted hosts, increment by
$2.4$ (drift $+0.08$), capped at 60~days.
\end{enumerate}
RNG seeds are derived from \texttt{(seed, window\_index)} so each
window is independently reproducible.

\subsection{Selection Policy}

HygienePrio-full's top-$K$ pairs drive fleet evolution at \textit{every}
window of every cell, for \textit{every} method evaluated at that window.
Each method is scored on the same evolving backlog; comparisons are
therefore conditional on the HygienePrio-driven trajectory. This avoids
the non-identifiability problem in which an EPSS-only-driven fleet and
a HygienePrio-driven fleet would evolve to different residual backlogs,
making subsequent method comparisons un-attributable. The choice and its
consequence are documented as an internal-validity threat in
\S\ref{sec:threats}.

\subsection{Decay Slope}

For each (cell, seed, method), we fit an ordinary least-squares line to
the six per-window P@50 values $(w, p_w)$, $w = 1, \ldots, 6$, and
record the slope $\hat\beta$. Negative slope indicates degrading
precision; $|\hat\beta|$ measures decay rate in units of P@50 per
window. Cell-level slope is reported as the mean of per-seed slopes with
a 95\% percentile bootstrap CI (10{,}000 resamples).

\subsection{Hypothesis Tests}

\textbf{H1 and H2.} For EPSS-only, we report Spearman $\rho$ between
slope and $K$ at each fixed $\lambda$ (H1) and between slope and
$\lambda$ at each fixed $K$ (H2)~\cite{spearman1904}. The pre-registered
threshold for ``monotone'' is $|\rho| \geq 0.8$.

\textbf{H3.} We compute the maximum $K/\lambda$ ratio at which the cell
slope satisfies $\hat\beta \geq -0.01$ and report it descriptively as
the steady-state boundary.

\textbf{H4.} We report W6 mean P@50 for HygienePrio-full at every cell
and check that all 20 cells satisfy mean $\geq 0.40$.
