\section{Experimental Setup}

\subsection{Pre-Registration}

The protocol --- including research questions, $(K, \lambda)$ grid,
hypotheses, statistical decision rules, and stop rules --- was fixed
before any sweep result was inspected. The full pre-registration protocol accompanies the reproducibility
artifact release.

\subsection{Calibration Procedure}

No calibration is performed in this study. Scorer weights
$(\alpha, \beta, \gamma, \delta) = (0.7, 0.5, 0.1, 0.2)$ and HRS
weights $(0.5, 0.3, 0.2)$ are reused verbatim from the prior
HygienePrio calibration~\cite{paper4hygieneprio}. This is intentional:
the question is how a \textit{fixed} HygienePrio configuration behaves
across operating regimes, not whether per-cell re-fitting could rescue
it. A prior recalibration ablation~\cite{paper5temporal} established
that per-window recalibration improves P@50 by up to $+21$~pp at fixed
$(K, \lambda)$; the present sweep isolates the regime-sensitivity
question.

\subsection{Sweep Execution}

For each (cell, seed, window):
\begin{enumerate}
\item Generate the Window-1 EEHDA fleet from the seed; this is
identical across cells because the cell-defining parameters affect only
the evolution, not the initial state.
\item Score all unpatched applicable pairs with each of the five methods.
\item Compute P@50, P@100, P@250 from the per-window ground-truth
labels (\S\ref{sec:problem}).
\item Persist one row per (cell, seed, window, method) to
\texttt{sweep\_results.csv}.
\item Advance the fleet using HygienePrio-full's top-$K$ pairs and a
Poisson$(\lambda)$ new-CVE disclosure draw.
\end{enumerate}

Total: 5 capacity levels $\times$ 4 arrival rates $\times$ 25 seeds
$\times$ 6 windows $\times$ 5 methods $= 15{,}000$ rows.

\subsection{Statistical Reporting}

Cell-level point estimates are means across the 25 evaluation seeds.
95\% confidence intervals are percentile bootstrap with 10{,}000
resamples~\cite{efron1994introduction}. Decay slopes are OLS-fit per
(cell, seed, method) and then aggregated as the per-seed mean with a
95\% percentile bootstrap CI. Spearman correlations for H1 and H2 are
computed on cell-mean slopes (5 points per slice for H1, 4 points per
slice for H2)~\cite{spearman1904}.

No null-hypothesis significance tests are reported; comparisons rely on
CI overlap and the pre-registered Spearman thresholds.

\subsection{Reproducibility}

The sweep driver, analysis script, and figure generator are released
under the MIT licence with the artifact. From the artifact root:
{\small\begin{verbatim}
PYTHONPATH=src python3 src/run_sweep.py
PYTHONPATH=src python3 src/analyze_sweep.py
PYTHONPATH=src python3 src/make_figures.py
\end{verbatim}}
The driver re-uses the multi-window simulator
of~\cite{paper5temporal} and the HygienePrio scorer
of~\cite{paper4hygieneprio} via \texttt{sys.path} injection (no code
copy). Determinism follows the per-(seed, window, step) RNG seeding
of~\cite{paper5temporal}.
