\section{Discussion}

\subsection{What the Sweep Adds to Paper~5}

Paper~5~\cite{paper5temporal} reported that EPSS-only collapses across
six windows at a single cell and concluded that hygiene augmentation
sustains prioritization quality. The present sweep confirms the
\textit{relative} portion of that conclusion --- HygienePrio-full beats
EPSS-only in $96.0\%$ of (cell, seed, window) triples --- but rejects
the \textit{absolute} portion at high capacity. The W6 P@50 floor
provided by hygiene augmentation is regime-dependent: at $K \leq 50$
it sits near $0.5$; at $K = 200$ it sits near $0.1$. A reader of
Paper~5 alone might assume HygienePrio-full delivers a high absolute
P@50 across operating points; the sweep shows this assumption is wrong
above $K = 100$.

\subsection{Why HygienePrio Collapses at High Capacity}

The mechanism is structurally identical to EPSS-only's collapse. At
each window, HygienePrio-full's top-$K$ selection is biased toward
high-EPSS pairs on high-HRS hosts. At $K = 200$, this preferentially
remediates the most exposed hosts en masse; their patch posture drops,
their telemetry freshness recovers, and they exit the
upper tail of the HRS distribution. By W3--W4, the recomputed HRS
75th-percentile threshold sits over a flatter distribution; by W5--W6,
the binary positive condition is satisfied by a small, low-signal
residual set with no discriminative structure left for HRS-based
scoring to recover. The same compositional effect that drains EPSS-only
also drains HygienePrio-full --- just at a higher capacity threshold.

\subsection{Operational Implications}

For an organisation operating at $K \leq 50$ pairs per bi-weekly window,
the Paper~5 conclusion stands: hygiene augmentation provides a high
absolute P@50 across windows, and is a strict improvement over EPSS-only.
For an organisation operating at $K \geq 100$, neither EPSS-only nor
HygienePrio-full delivers a high absolute P@50 by W6 --- but
HygienePrio-full remains strictly better than EPSS-only on the
overwhelming majority of pairs. The honest operational summary is:
\begin{itemize}
\item Use HygienePrio-full instead of EPSS-only at \textit{every}
capacity level studied --- the per-pair advantage is preserved.
\item Do not expect a high absolute W6 P@50 from any method at
$K \geq 100$ on the simulated bi-weekly cadence. The absolute floor
is regime-dependent and decays as a function of $K/\lambda$ for
both methods.
\item For comparison studies, report $(K, \lambda)$ explicitly and do
not claim ``HygienePrio retains $\sim 0.5$ P@50'' as a method-level
fact without qualifying the cell it was measured in.
\end{itemize}

\subsection{Why the Predicted Monotonicities Failed}

The protocol predicted clean monotone scaling of EPSS decay with $K$
and $\lambda$. The Spearman correlations show this is not what the
sweep produces. We do not attempt a post-hoc rescue. Two confounds
are visible in the data and we report them as the underlying mechanisms
rather than as failures of the prediction:

\textit{(i) Threshold drift confound.} The per-window-recomputed HRS
75th-percentile threshold shifts as patches are applied; at high $K$,
the threshold moves faster than at low $K$. EPSS-only's per-window
P@50 is computed against this moving positive set, not a fixed one.
Slope estimates therefore mix true compositional decay with
denominator-redefinition effects.

\textit{(ii) Selection-policy coupling.} All methods are evaluated on
the trajectory generated by HygienePrio-full's top-$K$ selections. At
high $K$, HygienePrio's preferences drive the fleet evolution
strongly, and EPSS-only's performance against that
evolved-by-someone-else backlog is not the same quantity as
EPSS-only's performance on a self-driven backlog. A fully factorial
``each method drives its own trajectory'' design would isolate
the EPSS decay rate from the selection-policy coupling, at the cost
of non-identifiable cross-method comparison; we discuss this as future
work below.

\subsection{Relationship to the Research Sequence}

Papers~1--5 progressively widened the evaluation lens. Paper~1
established a single-window null result for CVE-level augmentation;
Papers~3 and~4 identified hygiene signals as the missing factor;
Paper~5 added the temporal dimension at one cell. The present paper
adds the capacity-arrival dimension and recovers an honest
qualification: the absolute P@50 ceiling provided by hygiene
augmentation is regime-dependent, but the per-pair relative
advantage is regime-robust. This qualification matters for downstream
work that wishes to cite ``HygienePrio retains $\sim 0.5$ P@50''
without acknowledging the cell-dependence of that number.
