\section{Related Work}

\textbf{Single-cell temporal evaluation.} The prior temporal-stability
evaluation~\cite{paper5temporal} established the multi-window
evaluation framework at a single cell
$(K = 50, \lambda = 3)$ and demonstrated EPSS-only decay and
HygienePrio retention at that operating point. The present paper
generalises that result along the two cell-defining axes and recovers
a qualified picture: relative advantage is robust, absolute floor is not.

\textbf{Per-CVE EPSS dynamics.} Ravalico et al.~\cite{ravalico2025epsstemporal}
characterised the temporal stability of per-CVE EPSS scores across
$\sim 45{,}000$ CVEs. Their study examines the random walk of an
individual score; the present paper examines the compositional decay
of EPSS-as-a-ranking-signal under capacity-constrained remediation.
The two effects are independent; the compositional decay documented
here would occur even with perfectly stable per-CVE scores.

\textbf{Risk-based vulnerability management.}
Jacobs et al.~\cite{jacobs2020improving} demonstrated that
exploit-prediction models substantially outperform CVSS-based triage
on enterprise data. Their evaluation is at a single window. The
present paper does not contest that finding within Window~1 (EPSS-only
beats CVSS-only at every cell in our sweep at W1) but adds that
single-window comparative advantage does not survive to W6 in any
cell of the studied grid.

\textbf{Sensitivity studies in prioritization.} Sensitivity analyses
of vulnerability-prioritization methods to capacity and arrival rate
are uncommon in the open literature; most published comparisons fix
both. The present paper documents a case where the choice of
$(K, \lambda)$ would have changed the headline conclusion --- and
provides a frozen 15{,}000-row artifact for downstream
sensitivity-analysis work.

\textbf{Cyber-hygiene benchmarking.}
HygieneBench~\cite{paper3hygienebench} established the discriminative
structure of patch posture and AD group drift in synthetic
anomaly-detection tasks. HygienePrio~\cite{paper4hygieneprio}
integrated those signals into a scorer. Both are single-window studies. The present
paper inherits both as fixed inputs and varies the multi-window
operating point.

\textbf{Policy mandates.} CISA BOD 22-01~\cite{cisa2021bod2201} and
23-01~\cite{cisa2022bod2301}, together with NIST SP 800-40
Rev.~4~\cite{nist2022sp80040r4}, define the operational
window-scheduling regime that the sweep simulates. No prior work, to
our knowledge, reports a pre-registered two-dimensional capacity-arrival
sweep of prioritization methods under this regime with frozen seeds.
