\section{Conclusion}
\label{sec:conclusion}

A pre-registered two-dimensional sweep over remediation capacity $K$
and CVE arrival rate $\lambda$, evaluated on 25 seeds across six
maintenance windows and five prioritization methods, produces 15{,}000
result rows that revise the prior temporal-stability evaluation's single-cell conclusion in three
places.

\textbf{First}, EPSS-only Precision@50 decays in every cell of the
grid (slope $-0.013$ to $-0.064$ P@50/window). No cell studied
reaches steady state.

\textbf{Second}, the pre-registered monotonicity hypotheses (H1, H2)
are rejected: Spearman correlations between cell-mean slope and the
swept axes fall well short of the $|\rho| \geq 0.8$ threshold and
frequently carry the wrong sign. The underlying dynamics are
non-monotone in the synthetic regime studied, and we report this honestly
rather than smoothing.

\textbf{Third, and most importantly, the pre-registered claim that
HygienePrio-full retains a high absolute floor across all cells (H4)
is rejected.} At $K \in \{100, 200\}$, HygienePrio-full's W6 mean
P@50 collapses to $\{0.32, 0.07\}$ on average --- not because hygiene
signals fail to discriminate but because high-throughput remediation
exhausts the high-HRS tail of the fleet, leaving the residual backlog
with little discriminative structure for any host-level signal to
recover.

The robustness claim that survives the sweep is per-pair: across all
3{,}000 (cell, seed, window) comparisons, HygienePrio-full outperforms
EPSS-only at P@50 in $96.0\%$ of pairs (minimum per-cell $76.7\%$).
Hygiene augmentation is a strict improvement over EPSS-only across
the studied regimes, but is not a guarantee of high absolute scheduling
quality at high capacity. Future external comparison work --- including studies on online
recalibration and multi-window optimisation --- should report results
across $(K, \lambda)$ cells rather than at one operating point.

\textbf{Reproducibility.} The sweep driver, analysis script, pre-registration
protocol, and frozen 15{,}000-row results CSV are available at
\url{https://github.com/Harshavardhanmalla-Labs/research-papers/tree/main/paper6}.

\textbf{Future work.} The most important next steps are (i) a fully
factorial ``each method drives its own trajectory'' sweep to separate
intrinsic EPSS decay from selection-policy coupling, (ii) external
validation on real fleet telemetry where exploitation-event logs
replace HRS as ground truth, and (iii) integration with non-greedy
multi-window scheduling that explicitly models the $(K, \lambda)$
capacity-arrival balance as a planning input.
