\section{External Validity Under Real CVE Attribute Distributions}
\label{sec:external_validity}

The 96.0\% HygienePrio-vs-EPSS persistence finding (\S\ref{sec:results})
is bounded to the synthetic EEHDA attribute model. As with Paper~4,
we add a partial external-validity check by replacing the
synthetic per-CVE $(\mathrm{EPSS}, \mathrm{KEV})$ attribute fixtures
with samples from a frozen real-world snapshot of the CISA KEV catalog
and the FIRST.org EPSS feed (2026-06-05). Fleet topology, simulator,
capacity-arrival sweep mechanics, HRS components, scorer weights, and
ground-truth definition are unchanged; only the CVE attribute
distribution shifts.

The sweep is run on a focused subset of the original Paper~6 grid:
$K \in \{50, 100, 200\}$, $\lambda \in \{1, 3, 12\}$, 25 evaluation
seeds, 6 windows, 5 methods. Total rows: 6{,}750.

\input{tables/tab_external_validity}

\subsection{Honest Finding}

\textbf{The 96.0\% per-pair persistence is a synthetic-distribution
artifact.} Under real CVE attribute distributions, the overall
HygienePrio-full $>$ EPSS-only persistence across all
(cell, seed, window) triples falls from $96.0\%$ to $\mathbf{10.0\%}$.
The two methods tie (within $0.5$~pp) in $69\%$ of (cell, seed, window)
triples; EPSS-only is slightly ahead at $K = 50$ (cell-mean W6 gaps of
$1.3$--$2.3$~pp in its favour) and the two are essentially identical
at $K \geq 100$. Notably, all $135$ HygienePrio wins in the real sweep
occur at Window~1 only --- per-cell persistence is exactly $0.100$ in
all 9 cells. This is not a pipeline artifact: after W1 the two methods'
score distributions collapse onto the same residual backlog and produce
tied selections, so no post-W1 wins are possible.

\textbf{Why.} Two reinforcing mechanisms:

\textit{(i) Real EPSS distribution is thinner.} As documented in
Paper~4, \S XII~\cite{paper4hygieneprio} (real$\,\Rightarrow\,$3.64\%
EPSS$>0.10$ vs.\ synthetic 12\%), real CVE corpora produce a thinner
upper-EPSS tail. This makes the EPSS-only baseline less informative
in absolute terms but \emph{more concentrated} on the actual
ground-truth positives, so EPSS-only's relative discriminative power
improves. Under the EEHDA synthetic fixture, EPSS-only ranks 12\% of
the backlog above the labelling threshold, of which most are noise;
under real distributions only 3.64\% clear the threshold and they
are higher-quality.

\textit{(ii) Real KEV prevalence is much lower.} Real KEV coverage is
0.52\% vs.\ synthetic 8\%. The HygienePrio scorer's KEV-recency term
contributes far less under real distributions, weakening the
quantitative gap between HygienePrio and EPSS-only.

\subsection{What Survives}

\textbf{The qualitative capacity-collapse finding is preserved and
sharpened.} HygienePrio's W6 P@50 collapses at $K = 200$ in the real
distribution (mean $0.010$--$0.021$ across $\lambda$), \emph{just like
EPSS-only's collapse}. The Paper~6 H4 rejection (HygienePrio does not
retain an absolute floor at high capacity) is reproduced under real
distributions and is, if anything, more severe: at $K = 200$ in the
real sweep, all methods drop below $0.025$ at W6.

\textbf{HRS-only collapses to near-zero under real distributions.}
HRS-only's mean W6 P@50 is $0.000$--$0.002$ across all 9 cells. The
combination of thinner EPSS tail and lower KEV prevalence means the
ground-truth positive set (EPSS$>0.10$ AND HRS$>$75th percentile) is
small to begin with, and HRS-only's rankings cannot find the few
positives that exist.

\textbf{The compositional decay mechanism is robust.} Paper~6's
EPSS decay slope finding (universally negative across the grid) is
reproduced. The mechanism --- capacity-constrained remediation
drains the high-EPSS tail --- does not depend on synthetic
distribution and is, as expected, more aggressive under thinner
real-world tails for the hygiene-augmented method: HygienePrio-full's
W6 cell means in the real sweep are uniformly below their synthetic
counterparts. EPSS-only is the exception at $K = 50$, where its real
W6 cell means ($0.114$--$0.121$) are actually \emph{higher} than the
synthetic ones ($0.034$--$0.053$), consistent with the more
concentrated real upper-EPSS tail described above.

\subsection{Operational Implication}

Both Paper~4's $+31$~pp synthetic gap (Paper~4,
\S XII~\cite{paper4hygieneprio}) and Paper~6's 96\% per-pair
persistence are synthetic-distribution
effects. The honest cross-paper recommendation is:

\begin{itemize}
\item Single-window evaluations like Paper~4 should report the
real-distribution gap ($+2.4$~pp) as the substantive operational claim;
the $+31$~pp synthetic number is informative about the EEHDA
generator, not the field.

\item Multi-window evaluations like Paper~6 should re-attribute the
``HygienePrio wins'' claim under real distributions as: the two
methods tie (within $0.5$~pp) in $69\%$ of (cell, seed, window)
triples; EPSS-only is slightly ahead at $K = 50$ ($1.3$--$2.3$~pp at
W6) and the two are essentially identical at $K \geq 100$, with both
methods converging to near-zero at high capacity.

\item The structural finding --- capacity-driven collapse of any
deterministic scoring policy \emph{under self-driven (closed-loop)
selection} --- is robust across synthetic and real distributions,
and is the program's most generalisable result. This matches the
theoretical bound proven in Paper~9~\cite{paper9selftraj} as the
Closed-Loop Signal Exhaustion Theorem. Paper~9~\cite{paper9selftraj}
further shows the collapse is specific to self-driven selection and
does not occur under independent drivers.
\end{itemize}

\subsection{Honest Caveat on This Section's Scope}

The real-distribution test replaces only per-CVE attribute
distributions. The fleet topology, host--CVE assignment,
HRS components (patch posture, AD exposure, telemetry freshness),
ground-truth definition (EPSS$>0.10$ AND HRS$>$75th percentile),
and selection-policy convention are unchanged. A full external
validation would require longitudinal real-fleet exploitation
outcome data, which remains unavailable in any public dataset.
The present section is a partial external-validity bound, not a
full replacement for real-data validation.

\subsection{Reproducibility}

The \texttt{real\_data/} directory lives at the repository root
(a sibling of \texttt{paper6/}, not inside it):

{\small\begin{verbatim}
<repo-root>/real_data/real_dist_capacity_sweep.py
<repo-root>/real_data/results/
    real_dist_capacity_sweep.csv
<repo-root>/real_data/results/
    real_dist_capacity_summary.json
\end{verbatim}}
\noindent (6{,}750-row frozen sweep.) Reproduce from the repository
root with
\texttt{python3 real\_data/\allowbreak real\_dist\_capacity\_sweep.py}.
