Capacity-constrained vulnerability remediation teams must decide which (host, CVE) pairs to patch within each maintenance window, yet the dominant public triage signal --- the Exploit Prediction Scoring System (EPSS) --- is asset-agnostic by design: it estimates per-CVE exploit likelihood without regard to whether the affected host is actively managed, has high patch debt, or is exposed through privileged Active Directory (AD) relationships. Prior work found that augmenting EPSS with CVE-level features did not improve prioritization on a synthetic government-shaped fleet, suggesting that the missing signal is dynamic host-level hygiene posture rather than additional CVE-level features.

We present \textbf{HygienePrio}, a scoring framework that integrates a three-dimensional Hygiene Risk Score (HRS) --- capturing patch posture, AD exposure state, and telemetry freshness --- into an EPSS-weighted (host, CVE) pair prioritization scorer with an explicit interaction term. Weights are calibrated by pre-registered grid search on held-out fleet seeds.

In a pre-registered synthetic evaluation across 25 fleet seeds, HygienePrio achieves a mean Precision@50 of 0.509 compared with EPSS-only's 0.202 --- approximately 31 percentage-point improvement under capacity-constrained schedules, with non-overlapping BCa 95\% confidence intervals and improvement on all 25 of 25 evaluation seeds (synthetic evaluation only). Patch posture is the dominant hygiene dimension ($\approx$20 pp ablation drop at P@50), substantially exceeding the contributions of AD exposure ($\approx$9 pp) and telemetry freshness ($\approx$2 pp, overlapping confidence intervals).

To our knowledge, HygienePrio is the first scorer to jointly operationalize per-CVE exploit likelihood and host-level hygiene posture for remediation ordering in a pre-registered, reproducible evaluation framework. All claims are bounded to the synthetic evaluation context; generalization to real enterprise fleets requires external validation on real exploitation outcome data not performed here.
