\section{Experimental Setup}

\subsection{Evaluation Infrastructure}

All experiments are implemented in Python 3.11 using NumPy 1.26, Pandas 2.1, and scikit-learn 1.4 on a MacOS system (Apple M-series CPU, 16 GB RAM). Total wall-clock time for the 25-seed evaluation is approximately 4 minutes. Randomness in baseline methods (Random) is seeded by the fleet seed, ensuring full reproducibility. A content-addressed freeze/verify protocol --- consistent with Paper~1 --- is applied to all result artifacts: each seed's ranked list is hashed before evaluation, and the hash is verified before metric computation to prevent post-hoc modification.

\subsection{Calibrated Weights}

Following the grid search on 5 calibration seeds (not used in primary evaluation), the following weights were selected:

\begin{table}[!t]
  \caption{Calibrated scorer weights from grid search on held-out calibration seeds}
  \label{tab:calibrated_weights}
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Parameter} & \textbf{Calibrated Value} \\
    \midrule
    $\alpha$ (EPSS weight) & 0.7 \\
    $\beta$ (HRS weight) & 0.5 \\
    $\gamma$ (KEV\_recency weight) & 0.1 \\
    $\delta$ (interaction weight) & 0.2 \\
    \bottomrule
  \end{tabular}
\end{table}

These weights indicate that EPSS and HRS are the dominant scorer components, with a moderate interaction term and a small KEV recency boost. The relatively low $\gamma$ reflects the low KEV prevalence in the fixture ($\sim$8\%): the $\mathrm{KEV\_recency}$ term contributes meaningfully only for KEV-applicable pairs.

\subsection{Evaluation Procedure}

For each of the 25 evaluation seeds:

\begin{enumerate}
  \item Generate the EEHDA fleet tables deterministically from the seed.
  \item Compute $\mathrm{HRS}(h)$ for each host using pre-registered dimension weights ($w_1=0.5$, $w_2=0.3$, $w_3=0.2$).
  \item Compute $\mathrm{KEV\_recency}(c)$ for each CVE using fixed $\lambda = 0.05$.
  \item Score all $(h, c) \in V$ using calibrated weights.
  \item Generate ranked list $R$ by sorting descending by $S(h, c)$.
  \item Generate baseline ranked lists (EPSS-only, CVSS-only, Random, HRS-only) using identical $V$.
  \item Compute ground truth labels using the pre-registered definition (\S3.2).
  \item Compute P@$K$, NDCG@$K$, Oracle-gap for $K \in \{50, 100, 250\}$ for all methods. $K = 50$ represents a tight weekly maintenance window (approximately 1.4\% of the mean fleet of $\sim$3,480 applicable pairs); $K = 100$ a moderate bi-weekly window; $K = 250$ a broad monthly capacity. These values span the range typical of reported enterprise patch cadences~\cite{verizon2026dbir}.
  \item Hash and verify result artifacts.
\end{enumerate}

\subsection{Baselines}

\begin{table}[!t]
  \caption{Baseline and ablation methods evaluated}
  \label{tab:baselines}
  \centering
  \small
  \begin{tabular}{@{}p{2.8cm}p{5.3cm}@{}}
    \toprule
    \textbf{Method} & \textbf{Description} \\
    \midrule
    EPSS-only & Rank by $\mathrm{EPSS}(c)$ descending; primary comparison \\
    CVSS-only & Rank by CVSS v3.1 base score descending \\
    Random & Uniform random (seed-fixed) \\
    HRS-only & Rank by $\mathrm{HRS}(h)$ descending; tests host hygiene without CVE signal \\
    HygienePrio-full & Full scorer with calibrated weights \\
    HygienePrio-noInteraction & $\delta = 0$ (additive only; tests interaction term contribution) \\
    HygienePrio-noPatch & $w_1 = 0$ (patch posture removed from HRS) \\
    HygienePrio-noAD & $w_2 = 0$ (AD exposure removed from HRS) \\
    HygienePrio-noFreshness & $w_3 = 0$ (telemetry freshness removed from HRS) \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Reporting Convention}

All metrics are reported as mean $\pm$ 95\% BCa bootstrap confidence interval~\cite{efron1994introduction} (10,000 resamples) across 25 evaluation seeds. No null hypothesis significance testing is performed; evidence is based on BCa CI non-overlap. With 25 seeds and the observed seed-to-seed standard deviation of $\approx$0.06 for P@50, the evaluation has sufficient power to detect differences of $\geq$5 pp at 80\% power (estimated via the standard formula for paired comparisons): the headline 31 pp difference substantially exceeds this threshold. Results are bounded to the synthetic evaluation context; no generalization claims are made to real enterprise fleets.
