\section{Discussion}

\subsection{Why Hygiene Signals Help Where CVE-Level Features Alone Did Not}

VulnPrio found that adding CVE-level features --- asset criticality scores, endpoint exposure flags, KEV membership --- to EPSS did not improve prioritization over EPSS-only on the EEHDA fleet. HygienePrio's results suggest a complementary explanation: the features added in VulnPrio were primarily CVE-level or static host-role features, while the missing discriminative signal was dynamic, telemetry-derived host-level hygiene posture.

The structural difference is important. Knowing that a host is a domain controller (asset criticality signal from VulnPrio) provides some risk context, but it does not distinguish between a well-managed domain controller with current patches and telemetry, and a neglected domain controller with 60\% unpatched CVE debt, stale telemetry, and over-privileged group memberships. HRS captures this distinction; static asset criticality does not.

This observation is consistent with HygieneBench finding that ML methods add meaningful signal on patch-vulnerability hygiene (Task T5) and group-membership drift (Task T2)---precisely the dimensions HRS encodes. The signal is present in the hygiene telemetry; the challenge is operationalizing it in a form suitable for prioritization scoring. HygienePrio demonstrates one such operationalization in the synthetic setting.

\subsection{Why the Interaction Term Showed Equivocal Benefit}

The interaction term $\delta \times (\mathrm{EPSS}(c) \times \mathrm{HRS}(h))$ was theoretically motivated as a multiplicative risk amplifier for pairs where both exploit likelihood and hygiene risk are high. However, the ablation shows only $\approx$3 pp improvement at P@50 from including it (0.509 vs.\ 0.482), with substantially overlapping BCa CIs.

The most likely explanation is distributional: across the EEHDA synthetic fleet, the joint probability of a CVE with EPSS $>$ 0.10 \emph{and} a host with HRS in the top quartile is approximately 10--12\% of applicable pairs per seed, given a 6.2\% mean positive base rate. In this sparse regime, the additive terms $\alpha \times \mathrm{EPSS}(c)$ and $\beta \times \mathrm{HRS}(h)$ already provide strong discriminative signal. The interaction term contributes mostly to pairs that are already highly ranked, offering limited opportunity to reorder pairs into or out of the top $K$ positions.

This does not invalidate the theoretical motivation. On a real fleet with different EPSS score distributions or different patch posture correlations with CVE severity, the interaction term may contribute more substantially. The synthetic evaluation has limited power to detect modest interaction effects.

\subsection{Synthesis with Prior Work}

The HygienePrio result builds on two distinct strands of prior work:

\begin{enumerate}
  \item \textbf{VulnPrio~\cite{paper1vulnprio}:} Established the (host, CVE) prioritization problem, the EEHDA synthetic fleet, and the null result that CVE-level multi-factor models are statistically indistinguishable from EPSS-only on the EHD metric --- providing a reproducible benchmark, an honest null, and identification of the missing signal type.
  \item \textbf{HygieneBench~\cite{paper3hygienebench}:} Demonstrated that host-level hygiene signals (patch posture, AD group drift, telemetry staleness) carry discriminative structure detectable from synthetic fleet telemetry, with ML methods adding value specifically on Tasks T5 and T2 --- providing a hygiene anomaly benchmark and identification of the most informative hygiene dimensions.
  \item \textbf{HygienePrio (this paper):} Integrates these findings: hygiene signals operationalised as HRS, when added to EPSS-weighted prioritization, produce measurable P@$K$ improvement in the synthetic evaluation (31 pp at P@50; all 25 seeds).
\end{enumerate}

The progression illustrates that honest null results are scientifically productive. The VulnPrio null did not indicate that the prioritization problem is unsolvable; it identified that a particular feature set was insufficient. HygieneBench identified a more promising feature set. The present work operationalises that identification. Each step would have been undermined by p-hacking or post-hoc feature selection --- the pre-registration and content-addressed audit trails in each work are what make the progression interpretable.

\subsection{Practical Implications (Synthetic Evaluation Only)}

Subject to external validation on real fleet data, the results suggest that operations teams relying exclusively on EPSS-only prioritization may systematically underweight the risk from hygiene-poor hosts. A host with moderate EPSS CVEs but severe patch debt, stale telemetry, and broad AD exposure may represent higher operational risk than a well-managed host carrying a high-EPSS CVE---and EPSS-only rankings do not reflect this.

\textbf{Instrumentation priority.} The ablation results suggest a prioritization of hygiene signal investment: patch posture tracking ($\approx$20 pp contribution at P@50) should be instrumented before AD exposure breadth tracking ($\approx$9 pp) and before telemetry freshness monitoring ($\approx$2 pp marginal in the synthetic evaluation). This ordering is consistent with the CISA BOD 23-01 mandate hierarchy.

\textbf{Operational capacity context.} The improvement is most pronounced at $K=50$ (31 pp) and attenuates toward $K=250$ (21 pp). With a 6.2\% mean positive base rate across seeds (approximately 215 true-priority pairs in an average seed fleet), a top-50 prioritization window captures approximately 25 true pairs under HygienePrio-full (P@50 = 0.509) versus approximately 10 under EPSS-only (P@50 = 0.202) in this synthetic evaluation. The additional 15 pairs per maintenance window represent a substantial synthetic improvement---but whether this translates to real fleet operational impact requires prospective evaluation.

\textbf{Failure mode analysis.} HygienePrio-full outperforms EPSS-only on all 25 evaluation seeds, so there are no seeds in this evaluation where EPSS-only is preferred. However, the improvement is not uniform: the per-seed P@50 improvement ranges from $\approx$0.18 to $\approx$0.44 (from Fig.~\ref{fig:seed_scatter}). Seeds with smaller improvements likely represent fleet configurations where patch debt is more uniformly distributed (reducing HRS's discriminative power) or where EPSS scores cluster narrowly (reducing the interaction term's relevance). Identifying which fleet characteristics predict smaller benefits from HygienePrio is an important direction for sensitivity analysis on real data.

\subsection{Limitations}

\textbf{Synthetic data.} All results are from a synthetically generated fleet using structural priors from public sources (DBIR, NVD, CISA BOD). The synthetic fleet cannot capture the full heterogeneity of real enterprise environments. Results should not be interpreted as predictions for real fleet prioritization without external validation.

\textbf{Ground truth circularity.} The ground truth definition includes HRS $>$ 75th percentile as a labelling condition (\S3). This creates a structural advantage for methods that incorporate HRS. The pre-registration prevents post-hoc optimization, but independent ground truth from real exploitation outcomes would provide a circularity-free evaluation.

\textbf{Calibration instability.} Weight calibration on only 5 seeds (held out from 30 total) is a thin calibration set given the observed seed-to-seed variance. The calibrated weights $(\alpha, \beta, \gamma, \delta)$ may not generalize robustly. A larger calibration set would reduce calibration noise.

\textbf{Scorer linearity.} The HygienePrio scorer is a linear combination with one interaction term. Non-linear relationships between hygiene dimensions and remediation priority that may exist in real fleets are not captured.

\textbf{False positive cost.} P@$K$ does not account for the operational cost of acting on a false positive. Wasted remediation capacity directed at a non-priority pair is not merely neutral---it displaces another pair from the maintenance window. A metric that weights false positives by remediation cost would provide a more operationally realistic assessment.
