\section{Related Work}

This section situates HygienePrio within the broader literature on vulnerability management, host-context scoring, and cyber-hygiene measurement, supplementing the foundational background in \S2.

\textbf{Vulnerability scoring and exploit prediction.}
The Common Vulnerability Scoring System (CVSS)~\cite{first2019cvss} provides a standardised framework for assessing severity across Base, Temporal, and Environmental metrics. As a CVE-level signal, CVSS shares the asset-agnostic limitation of EPSS~\cite{jacobs2021epss}: it scores a vulnerability in isolation without regard to the maintenance state of the affected host. Jacobs et al.~\cite{jacobs2020improving} demonstrated that exploit-prediction models substantially outperform CVSS-based triage for reducing mean time to remediation on enterprise data. This foundational result motivates using EPSS as the primary exploit-likelihood signal in HygienePrio. The National Vulnerability Database (NVD)~\cite{nist2026nvd} serves as the primary aggregation point for CVSS scores and CVE metadata. Unlike the above work, which optimises exploit prediction as a standalone CVE-level signal, HygienePrio integrates exploit likelihood with host-level hygiene posture via an explicit interaction term, targeting the (host, CVE) pair rather than the CVE alone.

\textbf{Risk-based vulnerability management (RBVM).}
Commercial RBVM platforms---Tenable Lumin, Qualys TruRisk, and Rapid7 InsightVM---combine EPSS, CVSS, threat intelligence, and asset context in proprietary scoring models that address the same host-CVE pair prioritization problem as HygienePrio. These systems are closed and not independently reproducible; no comparison claims are made against them. The 2026 Verizon Data Breach Investigations Report~\cite{verizon2026dbir} documented that vulnerability exploitation surpassed stolen credentials as the leading breach entry point for the first time, underscoring the operational urgency of principled patch prioritization at scale.

\textbf{Capacity-constrained prioritization.}
Paper~1~\cite{paper1vulnprio} constructed a reproducible benchmark for (host, CVE) pair prioritization on a synthetic government-shaped fleet, evaluating thirteen strategies combining EPSS, CVSS, KEV membership, asset criticality, and endpoint exposure across thirty seeds. Its central finding was null: no CVE-level augmentation materially outperformed EPSS, attributing this to uncalibrated weights and the absence of host-level hygiene signals. HygienePrio directly addresses this gap by introducing a three-dimensional Hygiene Risk Score.

\textbf{Identity and access management (IAM) security.}
The foundational concepts of access control and identity state that underpin the Active Directory (AD) Exposure dimension of HRS are surveyed in Bertino \& Sandhu~\cite{bertino2005database}. AD-exposure-aware risk scoring has been proposed in the lateral movement risk literature; HygienePrio incorporates AD exposure as one of three HRS dimensions, operationalizing domain-privilege exposure as a host-level risk amplifier rather than as a standalone signal.

\textbf{Anomaly detection for hygiene monitoring.}
Aggarwal \& Sathe~\cite{aggarwal2015outlier} establish theoretical foundations for outlier ensemble methods applicable to cyber-hygiene anomaly detection. HygieneBench (Paper~3)~\cite{paper3hygienebench} applied eight such methods across seven hygiene monitoring tasks on a synthetic fleet, finding that rule baselines dominate 86.2\% of configurations but that patch-vulnerability hygiene (Task T5) and group-membership drift (Task T2) are exceptions where structured methods add meaningful signal. HygienePrio operationalises these two discriminative dimensions---patch posture and AD exposure---as the dominant components of HRS, grounded in HygieneBench's empirical findings.

\textbf{Telemetry freshness and policy mandates.}
CISA BOD 23-01~\cite{cisa2022bod2301} mandates 14-day asset discovery and 72-hour vulnerability data freshness for federal agencies, and NIST SP~800-53~\cite{nist2020sp80053r5} specifies continuous monitoring controls that depend on current telemetry. These policies encode the intuition that stale telemetry degrades risk assessment reliability. HygienePrio models telemetry freshness explicitly as the TelemetryFreshness component of HRS, formalizing the policy mandate as a quantitative host-level risk signal.

\textbf{Weight calibration methodology.}
The pre-registered evaluation design, seed-stratified BCa bootstrap confidence intervals~\cite{efron1994introduction}, and capacity-constrained scheduler are inherited from Paper~1~\cite{paper1vulnprio}; the calibration gate methodology is inherited from Paper~2. The threats taxonomy follows Wohlin et al.~\cite{wohlin2012experimentation}.

No prior work combines exploit-likelihood scoring with a multi-dimensional, telemetry-derived host hygiene score and an explicit interaction term in a pre-registered, reproducible evaluation on a synthetic fleet. HygienePrio is the first system to jointly operationalise patch posture, AD exposure, and telemetry freshness as a unified HRS integrated with EPSS for (host, CVE) pair prioritization.
