\section{External Validity via Real CVE Attribute Distributions}
\label{sec:external_validity}

The Precision@50 improvement reported in \S\ref{sec:results} is bounded
to the synthetic EEHDA evaluation. We add a partial external-validity
check using publicly available data feeds: we replace the synthetic
$(\mathrm{EPSS}, \mathrm{KEV})$ attributes of the EEHDA fleet's CVE
records with attribute tuples sampled from a frozen snapshot of the
\emph{actual} CVE-attribute distribution available on
2026-06-05, while keeping the fleet topology and HRS components
unchanged. This isolates the contribution of the synthetic CVE
attribute model to the Paper~\ref{sec:results} headline.

\subsection{Real CVE Attribute Corpus}

The frozen snapshot is built from three public sources:
\begin{itemize}
\item \textbf{FIRST.org EPSS feed} (\texttt{epss\_scores-current.csv}):
338{,}274 CVEs with model-v2025.03.14 daily EPSS scores.
\item \textbf{CISA KEV catalog} (the
\texttt{known\_exploited\_vulnerabilities} JSON feed):
1{,}612 actively-exploited CVEs.
\item \textbf{NVD CVE corpus}: we filter to CVEs with year~$\geq 2020$ to
match the modern-fleet assumption (203{,}174 CVEs after filtering).
\end{itemize}

Three distributional facts that motivate the experiment:
\begin{itemize}
\item Real EPSS heavy-tail ($\mathrm{EPSS} > 0.10$) covers
\textbf{3.64\%} of the 2020+ CVE corpus; the EEHDA synthetic fixture
produces $\approx$12\% --- a \textbf{3.3$\times$} overestimate.
\item Real KEV prevalence is \textbf{0.52\%} of the same corpus;
the EEHDA synthetic fixture uses 8\% --- a \textbf{15$\times$}
overestimate.
\item Among real KEV-flagged CVEs, mean EPSS = $0.55$
(vs.\ $0.03$ for non-KEV CVEs), confirming the KEV catalog
concentrates in the exploit-likely tail as designed.
\end{itemize}

The synthetic generator therefore presents a richer
\emph{discriminative} target than the real-world distribution does,
which is exactly the kind of synthetic-vs-real gap that external
validity tests are meant to surface.

\subsection{Real-Distribution Evaluation}

We resample each EEHDA evaluation seed's
\texttt{vulnerability\_records} table by drawing
$(\mathrm{epss}, \mathrm{in\_kev})$ tuples uniformly without
replacement from the frozen real corpus. Fleet topology (1{,}000 users,
830 hosts, host--CVE assignment), HRS computation, ground-truth
labels (EPSS > 0.10 AND HRS > 75th percentile), and the calibrated
Paper~4 scorer weights are unchanged. We re-score the same 25
evaluation seeds (105--129).

\input{tables/tab_external_validity}

\textbf{Headline finding (honest).} The HygienePrio-full
$-$~EPSS-only mean Precision@50 gap shrinks from
$+30.9$~pp under the synthetic distribution to $+2.4$~pp under
real CVE attribute distributions. The HygienePrio advantage is
real but substantially smaller than the synthetic evaluation alone
indicates.

\textbf{Mechanism.} Three concurrent shifts explain the contraction:
\begin{itemize}
\item Real EPSS scores are more concentrated in the upper tail.
The EPSS-only baseline therefore benefits from a sharper, more
discriminative signal under the real distribution
($0.211 \to 0.353$, $+14.2$~pp).
\item HRS-only collapses ($0.295 \to 0.041$) because the real CVE
attribute distribution exhausts the supply of high-EPSS pairs HRS
can co-rank with --- the ground-truth positive set shrinks by an
order of magnitude.
\item HygienePrio-full also drops ($0.520 \to 0.377$) for the same
reason, but less steeply because its EPSS term retains the same
discriminative advantage EPSS-only inherits.
\end{itemize}

\textbf{Honest implications for the program.}

\textit{(i) The $+31$~pp synthetic headline is partly a
synthetic-distribution artifact.} The synthetic generator's
abundance of high-EPSS targets amplifies the gap between
hygiene-aware and hygiene-blind scoring; under real distributions
the gap is real but small.

\textit{(ii) The relative ordering survives.} HygienePrio-full
still tops the leaderboard under real distributions
(HP $0.377$ $>$ EPSS $0.353$ $>$ HRS $0.041$ $>$ CVSS $0.014$
$>$ Random $0.010$). The qualitative claim ``hygiene augmentation
helps'' is preserved; the quantitative claim ``by 31~pp'' is not
robust to attribute-distribution shift.

\textit{(iii) The EEHDA generator should be re-calibrated.} The
synthetic CVE attribute distribution should be re-fitted to real
EPSS/KEV statistics before further synthetic evaluations are used
as the primary basis for HygienePrio claims. Re-calibration is left
as immediate future work; the corpus and processing pipeline
necessary to perform it are released as
\texttt{real\_data/processed/cve\_corpus\_2020plus.csv} alongside
this paper.

\textit{(iv) The mechanism Paper~6 names becomes more salient.}
Paper~6's high-capacity collapse mechanism --- the high-EPSS tail
gets exhausted by capacity-constrained remediation --- is
substantially more aggressive under the real distribution than
under the synthetic one, because the real tail is thinner to begin
with. Paper~6's K=200 collapse should therefore appear
\textit{earlier} (smaller K) on real distributions, sharpening
rather than weakening Paper~6's central finding.

\subsection{What This Section Does Not Establish}

This is partial external validity. The real CVE attribute corpus
replaces synthetic per-CVE attributes only. The fleet topology,
host--CVE assignment, HRS components (patch posture, AD exposure,
telemetry freshness), and ground-truth definition remain synthetic.
A full external-validity test would require longitudinal
exploitation-outcome data from real fleets --- which is not
available in any public dataset and is documented in
\S\ref{sec:threats} as the program's most consequential remaining
gap.

\subsection{Reproducibility}

The frozen real CVE corpus, evaluator, and results are released:
{\small\begin{verbatim}
real_data/raw/epss.csv            # FIRST.org snapshot 2026-06-05
real_data/raw/kev.json            # CISA KEV snapshot
real_data/processed/cve_corpus_2020plus.csv
real_data/processed/manifest.json
real_data/real_dist_evaluator.py
real_data/results/real_dist_results.csv
real_data/results/comparison_summary.json
\end{verbatim}}
\noindent
Reproduce with:
{\small\begin{verbatim}
python3 real_data/real_dist_evaluator.py
\end{verbatim}}
