\section{Adversarial Robustness: A Stackelberg Best-Response Analysis}
\label{sec:adversarial}

Vulnerability prioritization scoring is, in principle, a target for
strategic attackers: an adversary who knows the defender uses EPSS as a
ranking signal can attempt to influence published EPSS scores
(through PoC publication timing, social-media-driven exploit chatter,
or selective vulnerability disclosure on hosts the attacker has
already compromised) to redirect remediation resources. We formalise
this scenario as a Stackelberg game and quantify how HygienePrio's
hygiene-augmented scoring compares to EPSS-only under best-response
adversarial pressure.

\subsection{Threat Model}

A defender deploys a deterministic prioritization scorer $S$ committed
in advance. An attacker observes $S$ and chooses a \emph{gaming
fraction} $g \in [0, 1]$ representing the share of (host, CVE) pairs
whose EPSS attribute the attacker can inflate from its true value to a
high-but-plausible target value $\hat{\mathrm{EPSS}} = 0.55$
(approximately the central tendency of EPSS among CVEs that appear in
the CISA KEV catalog --- mean $0.49$, median $0.52$ in the frozen
corpus of \S\ref{sec:external_validity} --- chosen so the gamed pairs
become borderline-positive under EPSS-only ranking).

The attacker's strategic constraint is realism: at high $g$ the
defender would notice anomalous EPSS distributions and discount them.
We therefore study $g \in \{0, 0.05, 0.10, 0.15, 0.20, 0.30\}$ ---
gaming up to 30\% of the eligible pair pool.

The attacker's strategic preference is to target pairs whose hosts
are in the \emph{bottom half} of the HRS distribution. This is the
defender's worst case for HygienePrio: by attacking pairs at
low-hygiene-risk hosts, the attacker inflates EPSS in cells where
HygienePrio's HRS co-ranking can do the least to filter them. (If the
attacker instead targeted high-HRS hosts, the gamed pairs would
co-rank as positives, reinforcing rather than degrading HygienePrio's
top-K selection.)

\subsection{Defender's Three Strategies}

We evaluate the same calibrated Paper~4 weights for HygienePrio-full
and the two natural baselines:
\begin{itemize}
\item \textbf{HygienePrio-full}: scoring weights $(\alpha, \beta,
\gamma, \delta) = (0.7, 0.5, 0.1, 0.2)$, unchanged from \S5.
\item \textbf{EPSS-only}: pure exploit-likelihood ranking.
\item \textbf{HRS-only}: pure hygiene ranking, as a HRS-blind reference
that ignores EPSS entirely.
\end{itemize}

\subsection{Experimental Setup}

We run the same 25-seed set as the real-distribution evaluation
(105--129; \emph{not} the primary evaluation's 100--124, see
\S\ref{sec:external_validity}) at each of the six gaming levels,
yielding 450 result rows. The ground truth (EPSS$>0.10$ AND
HRS$>$75th percentile) is computed \emph{after} attacker gaming, so
gamed pairs become spurious positives under EPSS but only true
positives if their host happens to clear the HRS threshold ---
which by construction it does not for attacker-targeted pairs (bottom
50\% HRS hosts).

\input{tables/tab_adversarial}

\subsection{Results}

\textbf{Reconciling the $g=0$ row with Table~\ref{tab:precision_k}.}
The unattacked baselines in Table~\ref{tab:adversarial}
(HygienePrio-full $0.595$, EPSS-only $0.331$) are higher than the
primary-evaluation values ($0.509$ / $0.202$) for two identifiable
reasons in the released harness
(\texttt{real\_data/adversarial\_eval.py}): (a) the adversarial
harness restricts the eligible-pair pool to \emph{unpatched} pairs
only (\texttt{vr[\textasciitilde vr["patched"]]}), whereas the
primary evaluation ranks all generated (host, CVE) pairs --- removing
already-patched pairs raises the positive base rate among ranked
candidates and therefore lifts every method's Precision@50; and
(b) the harness uses the 105--129 seed set rather than the primary
100--124 set. The $g=0$ row is therefore the harness-internal
baseline for the manipulation sweep, not directly comparable to
Table~\ref{tab:precision_k}; all within-sweep deltas are computed
against it.

\textbf{HygienePrio degrades by $\leq 3$~pp at any attack level.}
Across $g \in [0, 0.30]$, HygienePrio-full's mean Precision@50 falls
from $0.595$ to $0.566$ --- a $-2.9$~pp drop at the strongest attack
tested. The HRS co-ranking filters gamed pairs because the attacker's
targets have low HRS by construction; HygienePrio's
HRS-component down-weights them despite the inflated EPSS.

\textbf{EPSS-only degrades by $-14$~pp at $g = 0.05$.} A 5\% gaming
attack is sufficient to collapse EPSS-only from $0.331$ to $0.195$
($-13.6$~pp) and the drop saturates near $-13.8$~pp at $g \geq 0.10$.
EPSS-only has no host-context information to filter gamed pairs and
ranks them in proportion to the inflated EPSS.

\textbf{The HygienePrio-vs-EPSS gap \emph{widens} under attack.}
The synthetic-distribution baseline gap is $+26.4$~pp at $g = 0$.
At $g = 0.05$ the gap grows to $+38.6$~pp; at $g = 0.30$ to $+37.4$~pp.
HygienePrio's relative advantage over EPSS-only is amplified, not
diminished, when an attacker is present.

\textbf{HRS-only is invariant under EPSS attack.} HRS-only's mean
P@50 is $0.284$ at every gaming level because HRS-only's scoring
ignores EPSS entirely. This is a methodological sanity check rather
than an operational recommendation --- HRS-only's absolute level is
below HygienePrio's at every gaming level studied.

\subsection{Interpretation}

The adversarial analysis demonstrates that hygiene augmentation
provides a security-relevant property that EPSS-only lacks:
\emph{robustness against a strategic adversary who can influence the
EPSS signal}. The hygiene side-channel acts as a co-ranking filter
that cross-checks exploit-likelihood claims against host-context
plausibility. A gamed pair on a low-HRS host is implausibly
high-priority and HygienePrio down-ranks it; a gamed pair on a
high-HRS host would be a true positive and HygienePrio would
correctly elevate it.

This is the canonical defender-advantage pattern in adversarial
security: orthogonal signals are robust precisely because the
attacker has to game both simultaneously. EPSS+HRS forces the
attacker to compromise the hygiene posture of the host as well as the
exploit-likelihood signal --- a substantially harder attack than
either alone.

\subsection{Honest Caveats}

\textit{(i) Synthetic distribution.} This analysis is on the EEHDA
synthetic fleet. Section~\ref{sec:external_validity} showed that the
synthetic EPSS distribution is heavier-tailed than reality. The
adversarial gap may shrink under real distributions for the same
mechanism: the EPSS-only baseline starts higher under real
distributions, so gaming has less room to inflate. We do not re-run
the adversarial sweep under the real distribution; the qualitative
finding (HygienePrio is dramatically more robust to EPSS gaming
than EPSS-only) is unlikely to reverse because the HRS-cross-check
mechanism is distribution-independent.

\textit{(ii) Attacker model is one-shot.} The attacker commits to $g$
before remediation begins; a multi-round adaptive attacker who
observes which gamed pairs got remediated could in principle improve.
Modelling adaptive attackers requires a different game-theoretic
framework and is left as future work.

\textit{(iii) Attack on HRS not modelled.} An attacker who can also
manipulate hygiene observables (false patch-state reports,
group-membership injection, telemetry-freshness fraud) would
undermine HygienePrio's HRS co-ranking. Modeling adversarial
manipulation of host-state telemetry is a substantial open problem;
the present analysis bounds the attacker to EPSS manipulation only.
The HRS-attack adversary is identified as the strongest plausible
threat to hygiene-augmented prioritization and is left as the most
important future-work direction in this section.

\subsection{Reproducibility}

The adversarial evaluator and frozen results are released under
\texttt{real\_data/} at the repository root (not under
\texttt{paper4/}):
\begin{verbatim}
real_data/adversarial_eval.py
real_data/results/adversarial_results.csv  (450 rows)
\end{verbatim}
Reproduce: \texttt{python3 real\_data/adversarial\_eval.py}.
