\section{Real-World Retrospective: What Would HygienePrio Have Done?}
\label{sec:retrospective}

The synthetic and real-distribution evaluations of
\S\S\ref{sec:results}--\ref{sec:adversarial} test HygienePrio on
distributional aggregates. We close the empirical evaluation with a
\emph{worked retrospective}: for ten high-profile CVEs of the past
seven years, we examine what HygienePrio would have produced relative
to EPSS-only at the moment of public disclosure, using the
present-day (2026-06-05) EPSS and KEV state as a stable late-life
reference.

\input{tables/tab_famous_cves}

\subsection{Observations}

\textbf{(i) EPSS catches major CVEs.} All ten high-profile CVEs have
present-day EPSS scores in $[0.9342, 0.9446]$ --- the top $0.04\%$ of
the EPSS distribution. Every one is in the CISA KEV catalog.
EPSS-only ranking would correctly elevate any of these CVEs to the
top of a fleet's prioritization queue. The first-order claim
``EPSS works for major CVEs'' is empirically supported by the
present-day data.

\textbf{(ii) Major CVEs leave EPSS no room to discriminate.}
The narrow EPSS range $[0.9342, 0.9446]$ across ten distinct
high-impact CVEs means EPSS-only's relative ranking among them is
essentially noise. A 2023 fleet on the day MOVEit Transfer was
disclosed (CVE-2023-34362, EPSS $= 0.9425$, KEV-added $2023$-$06$-$02$)
faced the question: \emph{which of our hosts running MOVEit
should we patch first?} EPSS-only provides no answer --- every
affected host has the same per-CVE score.

\textbf{(iii) HygienePrio's contribution is host-side discrimination.}
The Paper~4 scorer's EPSS$\cdot$HRS interaction term
$\delta \cdot (\mathrm{EPSS}(c) \cdot \mathrm{HRS}(h))$ multiplies
the high EPSS of a major CVE by the host's hygiene risk, breaking
the tie in favour of high-HRS hosts (high patch debt, high AD
exposure, stale telemetry). The HRS dimension that Paper~4
\S\ref{sec:results} identifies as most informative ---
\emph{patch posture} --- is exactly the dimension that captures
which hosts are likely to have a long-uncated MOVEit instance.
On a retrospective Log4Shell-style fleet sweep with thousands of
hosts running affected software, HygienePrio's ranking would
elevate the patch-debt-laden hosts first; EPSS-only would
return them in arbitrary order.

\textbf{(iv) The KEV signal arrives \emph{after} disclosure.} For
CVEs like Log4Shell (disclosed 2021-12-09, KEV-added 2021-12-10),
KEV inclusion lags disclosure by one day; for Heartbleed (disclosed
2014-04-07, KEV-added 2022-05-04) the KEV-added date is over
\emph{eight years} after disclosure --- a function of the KEV
catalog's 2021 inception, not of CVE risk. The HygienePrio
$\gamma \cdot \mathrm{KEV\_recency}(c)$ term contributes meaningfully
in the days after KEV inclusion; before KEV inclusion it does not
fire. EPSS scores, by contrast, are updated daily for every CVE
regardless of KEV status. The KEV term in HygienePrio is therefore
a \emph{lagging amplifier} of CVEs that EPSS has already flagged.

\subsection{The Realistic Operational Claim}

The empirical results across this paper, including the
\S\ref{sec:external_validity} real-distribution finding, support a
narrower operational claim than the $+31$~pp synthetic headline alone:

\begin{quote}
\emph{HygienePrio provides host-side discrimination among the high-EPSS
CVEs that EPSS-only treats as interchangeable. Under the real-world
distribution of CVE attributes, the relative advantage of HygienePrio
over EPSS-only is small in aggregate Precision@50 ($+2.4$ pp,
\S\ref{sec:external_validity}), but is operationally significant at
the moment of a major-CVE disclosure: it tells a remediation team
which of many vulnerable hosts to patch first.}
\end{quote}

This narrower claim is what the empirical evidence in this paper
actually supports, and it is the one we recommend a deploying
organisation use as the basis for selecting HygienePrio over
EPSS-only. The synthetic $+31$~pp gap, while real for the EEHDA
fleet model, overstates the aggregate-distribution benefit; the
host-side discrimination value at major-CVE moments is the more
defensible operational rationale.

\subsection{Honest Caveats}

\textit{(i) Late-life EPSS proxy for disclosure-time EPSS.}
The EPSS scores in Table~\ref{tab:famous_cves} are present-day
(2026-06-05) values, not the disclosure-time values. EPSS scores
evolve over time as exploitation evidence accumulates. The
direction of evolution for major CVEs is upward (toward 1.0 as
they receive widespread attention), so the disclosure-day EPSS for
these CVEs was generally lower than the present-day value. We use
the present-day value as a proxy because the FIRST.org public feed
provides current scores; historical EPSS trajectories require the
private FIRST historical archive.

\textit{(ii) Retrospective is anecdote, not evaluation.}
This subsection presents ten anecdotes about real CVEs to motivate
the operational claim. It is not a controlled evaluation. The
aggregate-distribution evaluation in \S\ref{sec:external_validity}
is the proper external-validity test.

\subsection{Reproducibility}

\begin{verbatim}
real_data/processed/famous_cves_snapshot.csv
\end{verbatim}
\noindent (10 CVEs with present-day EPSS, KEV date, and severity
description.) Built from the FIRST.org and CISA snapshots in
\texttt{real\_data/raw/}.
