\section{Problem Formulation}
\label{sec:problem}

\subsection{Setting (Inherited)}

EEHDA synthetic fleet, scorer Eq.~(\ref{eq:hp}), multi-window
simulator, $K \in \{50, 100, 200\}$ at $\lambda = 3$, 25 evaluation
seeds, 5 calibration seeds, six bi-weekly windows, all inherited from
Papers~4--8.

\subsection{Five Strategies}

\begin{description}
\item[\textsf{fixed}] Paper~4 weights at every window.
\item[\textsf{lag1}] Grid-search on calibration seeds at $w - 1$
(Paper~7 baseline).
\item[\textsf{adaptive}] At each $w \geq 2$, run the change-point
detector (\S5.2). If detector \textit{fires}, use \textsf{fixed};
otherwise use \textsf{lag1}.
\item[\textsf{gated}] Static capacity-conditional rule: use
\textsf{lag1} weights if $K \leq 100$, \textsf{fixed} otherwise. No
per-window decision.
\item[\textsf{offline}] Paper~7 ceiling: grid-search on calibration
seeds at $w$.
\end{description}

\subsection{Pre-Registered Hypotheses}

\begin{description}
\item[H1] At $K = 200$, \textsf{adaptive} $\geq$ \textsf{fixed} at
every $w \geq 2$ (within $-0.01$ tolerance). \textit{Adaptive does
not harm relative to fixed at high capacity.}
\item[H2] At $K \in \{50, 100\}$, $|\textsf{adaptive} - \textsf{lag1}|
\leq 0.02$ at every $w \geq 2$. \textit{Adaptive preserves
moderate-capacity recovery.}
\item[H3] Change-point firing fraction is monotone in $K$ (Spearman
$\rho \geq +0.8$ between $K$ and firing fraction). \textit{Detector
fires more often at higher capacity.}
\item[H4] At $K = 200$, cell-mean P@50 of \textsf{adaptive} $\geq$
cell-mean of \textsf{gated}. \textit{Adaptive beats the static gate.}
\end{description}

\subsection{Ground Truth and Metric}

Inherited from Papers~5--8: (EPSS $> 0.10$) $\wedge$ (HRS $>$ 75th
percentile per window); P@50 measured against the resulting positive
set.

Stop rules and the full protocol are archived at
\texttt{paper10/design/PAPER10\_PROTOCOL.md}.
