\section{Experimental Setup}

\subsection{Pre-Registration}

Strategies, detector, threshold $\tau = 0.05$, gated capacity
threshold 100, hypotheses H1--H4, decision rules, and stop rules were
locked in
\texttt{paper10/design/PAPER10\_PROTOCOL.md} before any
adaptive-calibration result was computed.

\subsection{Execution}

For each $K \in \{50, 100, 200\}$:
\begin{enumerate}
\item Cache per-window $(\text{pairs}_w, \text{HRS}_w)$ states for
the five calibration seeds under fixed-weight HygienePrio-full
trajectory.
\item Cache per-window states for the 25 evaluation seeds (same
trajectory policy).
\item For each window $w = 1, \ldots, 6$, run the detector (\S5.2),
choose \textsf{adaptive}, \textsf{gated}, and \textsf{offline}
weights per \S5.3 and the calibration grid search; score every
evaluation seed at window $w$ with each of five strategies; record
one P@50 row per (seed, window, strategy) and one change-point
decision row per (cell, window).
\end{enumerate}

\subsection{Statistical Reporting}

Cell-mean point estimates are means across 25 evaluation seeds. 95\%
confidence intervals are percentile bootstrap with 10{,}000
resamples~\cite{efron1994introduction}. No null-hypothesis significance
tests; hypothesis decisions follow the pre-registered tolerance
thresholds. H3 is the only hypothesis with a correlation test
(Spearman~$\rho$ across three $K$ values; small sample size limits
the precision and is noted in \S\ref{sec:threats}).

\subsection{Reproducibility}

From \texttt{paper10/}:
{\small\begin{verbatim}
PYTHONPATH=src python3 src/run_adaptive.py
PYTHONPATH=src python3 src/analyze.py
PYTHONPATH=src python3 src/make_figures.py
\end{verbatim}}
The runner reuses Paper~5's window simulator and Paper~4's scorer
via \texttt{sys.path} injection. Deterministic from the seed list.
