\section{The AutoHeal Architecture}
\label{sec:architecture}

AutoHeal is a seven-stage closed-loop pipeline executed per maintenance
window. All stage parameters are pre-registered in
\texttt{paper10/design/PAPER10\_PROTOCOL.md} and frozen before any
evaluation-seed AutoHeal result was inspected.
Fig.~\ref{fig:architecture} shows the pipeline with its safety-bound
checks and the closed loop back to detection.

\input{tables/tab_architecture}

\begin{figure}[!t]
  \centering
  \begin{tikzpicture}[
      font=\scriptsize,
      stage/.style={draw, rounded corners=2pt, minimum width=2.5cm,
        minimum height=0.52cm, align=center, inner sep=2pt},
      safety/.style={draw, dashed, rounded corners=2pt, align=center,
        inner sep=2pt, minimum height=0.52cm},
      arr/.style={-{Stealth[length=2mm]}},
      node distance=0.28cm and 0.55cm]
    \node[stage] (detect) {1.~Detect\\ \tiny unpatched (host, CVE) pairs};
    \node[stage, below=of detect] (score) {2.~Score\\ \tiny HygienePrio + lag-1 calib.};
    \node[stage, below=of score] (triage) {3.~Triage\\ \tiny AUTO / REVIEW / DEFER};
    \node[stage, below=of triage] (plan) {4.~Plan\\ \tiny top-$K$ from AUTO bucket};
    \node[stage, below=of plan] (act) {5.~Act\\ \tiny simulated patch action};
    \node[stage, below=of act] (verify) {6.~Verify + Rollback\\ \tiny post-action health check};
    \node[stage, below=of verify] (learn) {7.~Learn\\ \tiny outcome-driven recalibration};
    \draw[arr] (detect) -- (score);
    \draw[arr] (score) -- (triage);
    \draw[arr] (triage) -- (plan);
    \draw[arr] (plan) -- (act);
    \draw[arr] (act) -- (verify);
    \draw[arr] (verify) -- (learn);
    % safety checks
    \node[safety, right=of verify, xshift=-0.1cm] (safe)
      {Safety bounds:\\ rollback ${>}10\%$ flag\\ cascade detection};
    \draw[arr, dashed] (verify) -- (safe);
    \draw[arr, dashed] (safe.north) |- node[pos=0.85, above, font=\tiny]
      {flag: suppress new-CVE intake} (detect.east);
    % closed loop
    \draw[arr] (learn.west) -- ++(-0.5,0) |- node[pos=0.25, left,
      font=\tiny, align=center] {next\\ window} (detect.west);
  \end{tikzpicture}
  \caption{The AutoHeal seven-stage closed-loop pipeline. Solid
  arrows: per-window data flow; the Learn stage closes the loop into
  the next window's Detect stage. Dashed: the pre-registered safety
  bounds (per-window rollback rate ${>}10\%$; cascading-failure
  detection), which in the simulated evaluation flag the window and
  suppress new-CVE intake (\S\ref{sec:safety_bounds}).}
  \label{fig:architecture}
\end{figure}

\subsection{Stage 1 — Detect}

Scan the fleet's vulnerability records; identify unpatched
(host, CVE) pairs. CVE attribute lookup uses the real EPSS / KEV
public corpus (\S\ref{sec:dataset}) so the same CVE in two hosts
has the same external-feed attributes.

\subsection{Stage 2 — Score}

Apply HygienePrio~\cite{paper4hygieneprio} with the calibrated
Paper~4 weights $(\alpha, \beta, \gamma, \delta) = (0.7, 0.5, 0.1,
0.2)$. At capacity $K \leq 100$, online calibration follows
Paper~7's lag-1 recipe~\cite{paper7online}; at $K = 200$, weights
are held fixed per Paper~7's K=200 hazard finding. The scorer
output is normalised to $[0, 1]$ to feed the triage thresholds.

\subsection{Stage 3 — Triage}

Each (host, CVE) pair is classified into one of three buckets via
the pre-registered rule:

\begin{itemize}
\item \textbf{AUTO} (auto-remediate): score $\geq 0.80$ AND
host criticality $\neq$ CRITICAL AND patch-test-suite present AND
no known blocking config AND not during business-hours window.
\item \textbf{REVIEW} (human-in-loop): score in $[0.50, 0.80)$ OR
host criticality = CRITICAL OR business-hours.
\item \textbf{DEFER}: score $< 0.50$ OR known incompatible patch.
\end{itemize}

The two thresholds (0.80, 0.50) and the CRITICAL gate are the
pre-registered configuration. They are deliberately conservative:
AutoHeal only auto-acts on high-confidence, low-risk pairs.

\subsection{Stage 4 — Plan}

From the AUTO bucket, select the top-$K$ pairs by HygienePrio
score (where $K$ is the per-window capacity). This is the
Paper~6~\cite{paper6capacity} capacity-constrained selection.

\subsection{Stage 5 — Act}

Each scheduled pair undergoes a simulated patch action with a
pre-registered failure-mode distribution drawn from public
sysadmin literature on production patch operations:
\begin{itemize}
\item SUCCESS: $92\%$
\item ROLLBACK (post-patch health-check fail): $5\%$
\item DEFERRED (patch blocked at install time): $3\%$
\end{itemize}

The numbers are fixed before evaluation. Real-world deployments
would condition on package, OS, and patch type; AutoHeal's
synthetic evaluation assumes the pre-registered distribution to
keep the threat model identifiable. The empirically observed
per-window rollback rates are reported in \S\ref{sec:results}
(they exceed the expected $5\%$ in small AUTO buckets).

\subsection{Stage 6 — Verify + Rollback}

Each acted pair runs a post-action health check. On failure, the
patch is reverted and the pair is re-classified as REVIEW for the
next window. The framework tracks per-window rollback rate; if
$> 10\%$ the hard-stop safety bound is \emph{flagged} for that
window. A cascading-failure detector
additionally fires if more than 5 rollbacks share a common
upstream patch ancestor (approximated by CVE id prefix). The
response to a flag in the simulated evaluation is described in
\S\ref{sec:safety_bounds}.

\subsection{Stage 7 — Learn}

Successful and rolled-back outcomes feed the Paper~7 lag-1
calibration update (when $K \leq 100$). At $K = 200$, weights are
held fixed per Paper~7's K=200 hazard finding, and the
learn stage records data for offline rebaselining only.

\subsection{Pre-Registered Safety Bounds}
\label{sec:safety_bounds}

Two safety bounds are pre-registered:

\begin{itemize}
\item Rollback rate $> 10\%$ at any window.
\item Cascading-failure detection ($> 5$ rollbacks share a common
patch ancestor).
\end{itemize}

\textbf{Detection vs.\ enforcement.} In the evaluated
implementation, exceeding either bound \emph{flags} the affected
window in the frozen results (134 window-level flags across the
sweep: 44 at $K = 50$, 44 at $K = 100$, 46 at $K = 200$) and
suppresses new-CVE intake for that window; remediation of the
existing backlog continues in subsequent windows. A production
deployment would escalate a flagged window to human review. The
protocol registered a stronger enforcement response (hard stop with
fallback to human-in-loop for remaining windows); that enforcement
path was \emph{not exercised} in the simulation --- the evaluation
measures detection of the safety bounds, not the operational
consequences of enforcing them. This deviation is disclosed in
\S\ref{sec:results} and discussed as an evaluation limitation in
\S\ref{sec:threats}.
