\section{Methodology}

\subsection{Three Strategies}

We evaluate three strategies on the same fleet trajectory per seed:

\textbf{AutoHeal} — the full seven-stage pipeline described in
\S\ref{sec:architecture}.

\textbf{Human-in-loop baseline} — every (host, CVE) pair is treated
as REVIEW; the team manually selects the top-30 pairs per window
(matching the 2026 DBIR survey baseline for human triage capacity)
ordered by HygienePrio score. The 30-pair budget is fixed
regardless of the cell's capacity $K$. No safety hard-stops;
rollbacks are absorbed by the manual process.

\textbf{Fixed-policy baseline} — same capacity $K$ as AutoHeal, no
triage step (all top-$K$ pairs by HygienePrio score are acted on),
no rollback escalation. This isolates the value of AutoHeal's
triage + safety machinery relative to a calibrated-scoring-with-no-gating
control.

\subsection{Per-Window Metrics}

For each (cell, seed, window) we record:

\begin{itemize}
\item $n_{\text{pairs}}$, $n_{\text{auto}}$, $n_{\text{review}}$,
$n_{\text{defer}}$: counts after triage.
\item $n_{\text{acted}}$, $n_{\text{success}}$, $n_{\text{rollback}}$,
$n_{\text{defer-at-act}}$: counts after acting.
\item Rollback rate $= n_{\text{rollback}} / n_{\text{acted}}$.
\item Mean time-to-remediate (MTTR), measured in windows from
disclosure to successful remediation, averaged over successes in
the current window.
\item Coverage-to-date: fraction of all EPSS$>0.5$ pairs
cumulatively remediated.
\item Cascade-detected and safety-bound-flagged booleans (the
\texttt{halt\_triggered} column of the frozen CSV records the
flag; see \S\ref{sec:safety_bounds}).
\end{itemize}

\subsection{Pre-Registered Hypothesis Tests}

\textbf{H1 (Coverage).} AutoHeal's cell-mean coverage at Window~6
(a 12-week horizon) is $\geq 0.80$ at $K \in \{50, 100\}$.
$K = 200$ is excluded from H1 by Paper~9 Corollary~4: at that
capacity, closed-loop calibration is structurally unable to escape
the signal-exhaustion bound, so a coverage hypothesis is not
warranted.

\textbf{H2 (Safety).} Per-window rollback rate $\leq 5\%$ at every
(cell, seed, window) triple. The hard-stop threshold (10\%) is
twice the H2 threshold; H2 is the operational target, the hard-stop
is the safety bound.

\textbf{H3 (MTTR Reduction).} AutoHeal's cell-mean MTTR for KEV-listed
CVEs is $\leq 50\%$ of the Human-in-loop baseline's MTTR at
$K \in \{50, 100\}$.

\textbf{H4 (Per-Pair Dominance).} As registered in the protocol,
AutoHeal beats Human-in-loop on \emph{Precision@50} in
$\geq 80\%$ of (cell, seed, window) triples at $K \leq 100$. The
analysis code evaluated the hypothesis on \emph{per-window coverage}
dominance instead, and Precision@50 was not instrumented in the
frozen per-window results; the paper therefore reports the
coverage-dominance version. This deviation from the registered
metric is disclosed in \S\ref{sec:results}.

\subsection{Statistical Reporting}
\label{sec:stat_reporting}

Cell-mean point estimates are means across the 25 evaluation seeds.
No null-hypothesis significance tests are performed; hypothesis
decisions follow the pre-registered tolerance thresholds.
Seed-level spread is available in the frozen artifact.

\subsection{Reproducibility}

From \texttt{paper10/}:
{\small\begin{verbatim}
PYTHONPATH=src python3 src/run_autoheal.py
PYTHONPATH=src python3 src/analyze.py
\end{verbatim}}
Re-uses Paper~4's \texttt{hygieneprio}~\cite{paper4hygieneprio} and
Paper~5's
\texttt{window\_sim}~\cite{paper5temporal} via \texttt{sys.path}; reads
the real corpus from \texttt{real\_data/processed/}.
