\section{Results}
\label{sec:results}

All claims trace to \texttt{paper10/results/primary\_v1/autoheal\_results.csv}
(2{,}700 rows) and the derived \texttt{hypothesis\_summary.json}.

\input{tables/tab_hypotheses}

\input{tables/tab_summary}

\subsection{H1 — Coverage Supported}

At Window~6 (14-day horizon), AutoHeal achieves cell-mean
coverage-to-date:
\begin{itemize}
\item $K = 50$: $\bar{c}_6 = 0.978$
\item $K = 100$: $\bar{c}_6 = 0.978$
\end{itemize}
Both exceed the pre-registered $\geq 0.80$ threshold by approximately
$18$~pp. By Window~12 the cell-mean coverage reaches $0.999$ at
both capacities --- effectively complete remediation of the
high-EPSS backlog. H1 is supported.

The substantive finding is that AutoHeal's \emph{eventual}
remediation completeness is high under the pre-registered
configuration. The autonomous-remediation core of the framework
works: vulnerable pairs are detected, scored, triaged, acted on,
verified, and successfully closed at high rates within 12 windows
(28 simulated days).

\subsection{H2 — Safety Bound Violated}

The pre-registered safety bound ($\leq 5\%$ rollback rate per
cell-seed-window) is violated at \textbf{300 of the 900 post-W1
window-seed cells} ($33.3\%$). The maximum per-window rollback
rate observed is $1.0$ ($100\%$) at small AUTO buckets where a
single rollback constitutes the entire action set.

The safety hard-stop ($> 10\%$ rollback per window) fires
\textbf{134 times} across the 900 cell-seed-window space
($14.9\%$); cascading failures are detected three times.
Halt counts split essentially evenly across capacities (44 at $K = 50$,
44 at $K = 100$, 46 at $K = 200$).

\textbf{Important methodological observation.} The H2 violation
is \emph{not} a failure of the safety mechanism --- the safety
mechanism correctly halted the pipeline 134 times. The
violation is that the H2 tolerance ($5\%$) was set assuming
stable per-window rollback rates from the pre-registered
failure-mode distribution. In practice, the conservative triage
threshold ($0.80$ for AUTO classification) produces small AUTO
buckets, and a single rollback in a small bucket gives a large
per-window rate. The pre-registration could be re-locked at a
larger tolerance (e.g., $\leq 15\%$ per window) consistent with
the observed empirical distribution; doing so within this paper
would be post-hoc tuning and is left as future work.

\subsection{H3 — MTTR Not Analysable}

The MTTR instrumentation records the disclosure window at the
moment of successful remediation rather than at the moment of
detection. Cell-mean MTTR for both AutoHeal and Human-in-loop is
$0.0$ windows --- a degenerate measurement.

We report this honestly per the protocol's stop rule. H3 cannot
be evaluated from this run; a corrected instrumentation
(disclosure window tracked at detection time) is pre-registered
for the follow-up evaluation. The instrumentation bug does not
affect H1, H2, or H4: those hypotheses depend on coverage,
rollback rate, and dominance fraction respectively, none of which
share the MTTR tracking code path.

\subsection{H4 — Dominance Rejected}

AutoHeal's coverage exceeds Human-in-loop's coverage in
$\textbf{2\%}$ of (cell, seed, window) triples at $K \in \{50, 100\}$
(6 of 300 triples at each $K$). The pre-registered $\geq 80\%$
dominance threshold is missed by 78~pp.

\textbf{Mechanism.} Human-in-loop unconditionally acts on 30 pairs
per window (matching the Verizon 2026 DBIR human triage capacity
calibration). AutoHeal at $K = 50$ with the conservative triage
threshold averages $\approx 27$ acted pairs per window, slightly
\emph{less} than Human-in-loop. Combined with the 134 hard-stop
halts (each halt zeroing AutoHeal's window throughput),
AutoHeal's effective per-window throughput is reduced relative to
the unconditional Human-in-loop baseline.

The H4 rejection is structural and predictable from the
pre-registered configuration: AutoHeal trades raw throughput for
safety-bounded automation, while Human-in-loop trades safety for
throughput.

\subsection{Cell-Mean Outcomes by Strategy}

Table~\ref{tab:summary} reports cell-mean outcomes at W12. The
substantive picture:
\begin{itemize}
\item AutoHeal achieves near-complete coverage ($0.999$) at
all three $K$ but with reduced per-window throughput
($26$--$36$ pairs/window) due to the strict triage threshold
and safety hard-stops.
\item Fixed-policy achieves near-complete coverage with full
throughput ($K$ pairs/window) but no safety hard-stop. At
$K = 200$ the post-W2 throughput drops dramatically ($4.2$ acted
pairs/window mean) because the high-EPSS backlog is exhausted
after early-window aggressive remediation.
\item Human-in-loop achieves near-complete coverage with stable
throughput ($30$ pairs/window).
\end{itemize}

\subsection{Pre-Registration Deviations}

None. The architecture parameters, hypotheses H1--H4, decision
rules, and stop rules were applied verbatim. The H2 violation, the
H4 rejection, and the H3 instrumentation issue are all reported
as observed; the abstract was rewritten per the protocol's stop
rule when H2 was rejected.
