\section{Related Work}

\textbf{Static gate and capacity-aware detector.} Paper~12 introduced
the static gate as a baseline and showed the capacity-aware
magnitude detector~\cite{paper12capaware} approximates it. This
paper is the first to beat the static gate in the Papers~7--13
calibration arc.

\textbf{CUSUM.} The classical one-sided CUSUM~\cite{page1954cusum}
is the standard online change-point detector. Two-sided CUSUM,
EWMA-CUSUM, and the more recent Bayesian online change-point
methods extend the classical procedure; all are out of scope for
this paper, which evaluates the simplest member of the family with
pre-registered parameters.

\textbf{Paper 11 sensitivity bound.} Paper~11~\cite{paper11tau}
showed that no single-$\tau$ magnitude detector reaches the joint
feasibility region. CUSUM converts the threshold-only design into
a (slack, threshold) family that this paper exercises at one
point, leaving the two-dimensional sensitivity sweep to future work.

\textbf{Multi-paper sequence.} HygieneBench
(Paper~3)~\cite{paper3hygienebench}, HygienePrio
(Paper~4)~\cite{paper4hygieneprio}, Temporal Stability
(Paper~5)~\cite{paper5temporal}, Capacity-Indexed Decay
(Paper~6)~\cite{paper6capacity}, Online Calibration
(Paper~7)~\cite{paper7online}, Multi-History Calibration
(Paper~8)~\cite{paper8multi}, Self-Trajectory
(Paper~9)~\cite{paper9selftraj}, Adaptive Recalibration
(Paper~10)~\cite{paper10adaptive}, Threshold Sensitivity
(Paper~11), and Capacity-Aware Threshold (Paper~12) form the
methodological substrate.

\textbf{Policy mandates.} CISA BOD~22-01~\cite{cisa2021bod2201},
23-01~\cite{cisa2022bod2301}, NIST SP~800-40~\cite{nist2022sp80040r4},
2026 DBIR~\cite{verizon2026dbir}.
