\section{Problem Formulation}
\label{sec:problem}

\subsection{Setting (Inherited)}

EEHDA synthetic fleet, scorer Eq.~(\ref{eq:hp}), multi-window
simulator, $K \in \{50, 100, 200\}$, $\lambda = 3$, six windows,
25 evaluation seeds, 5 calibration seeds, inherited from
Papers~4--11.

\subsection{Six Strategies}

\begin{description}
\item[\textsf{fixed}] Paper 4 weights, no refit.
\item[\textsf{lag1}] Paper 7 baseline grid-search on calibration
seeds at $w - 1$.
\item[\textsf{adaptive05}] Paper 10 single-$\tau$ adaptive at
$\tau = 0.05$ (Paper 11 baseline; included as a control).
\item[\textsf{cap\_aware}] Adaptive with per-$K$ threshold
$\tau_K$ pre-registered as $\{50: 0.20, 100: 0.05, 200: 0.02\}$.
\item[\textsf{gated}] Static rule ($K \leq 100 \to$ lag1; $K \geq
200 \to$ fixed).
\item[\textsf{offline}] Paper 7 ceiling: grid-search at $w$ on
calibration seeds.
\end{description}

\subsection{Pre-Registered Hypotheses}

\begin{description}
\item[H1] \textsf{cap\_aware} reaches the joint feasibility region:
worst per-window $\Delta^{\mathrm{cap-fix}}_{K=200} \geq -0.01$
AND cell-mean $\Delta^{\mathrm{cap-lag1}}_{K=50} \geq -0.02$
AND cell-mean $\Delta^{\mathrm{cap-lag1}}_{K=100} \geq -0.02$.
\textit{Capacity-aware reaches all three Paper 10 / Paper 11
pre-registered tolerances simultaneously.}
\item[H2] \textsf{cap\_aware} cell-mean P@50 $\geq$
\textsf{adaptive05} cell-mean P@50 at every (K, $w \geq 2$) within
$+0.01$ tolerance for noise. \textit{Capacity-aware is at least as
good as the single-$\tau$ control.}
\item[H3] \textsf{cap\_aware} fire fraction is monotone non-decreasing
in K: Spearman$(K, $ fire frac$) \geq +0.8$. \textit{Large $\tau_{50}$
fires least; small $\tau_{200}$ fires most.}
\item[H4] \textsf{cap\_aware} cell-mean P@50 at K=200 $\geq$
\textsf{gated} by $+0.01$. \textit{Capacity-aware delivers
operationally meaningful gain over static gating at the high-capacity
extreme.}
\end{description}

\subsection{Stop Rule}

If H1 is rejected, the abstract leads with the negative
``capacity-aware is also insufficient'' result before the discussion
is drafted, per the protocol.
