\section{Methodology}

\subsection{Scorer (Inherited)}

\begin{equation}
\begin{aligned}
S(h,c) =\;& \alpha\,\mathrm{EPSS}(c) + \beta\,\mathrm{HRS}(h) \\
          & + \gamma\,\mathrm{KEV\_recency}(c) \\
          & + \delta\,\bigl(\mathrm{EPSS}(c) \cdot \mathrm{HRS}(h)\bigr).
\end{aligned}
\label{eq:hp}
\end{equation}

\subsection{Capacity-Aware Detector}

At window $w \geq 2$, the detector computes $|\Delta_w|$ (Paper 10
\S5.2) and compares against the per-$K$ threshold:
\begin{equation}
\textsf{cap\_aware fires at } w \iff |\Delta_w| \geq \tau_K.
\end{equation}
The threshold vector $\tau_K = \{50: 0.20, 100: 0.05, 200: 0.02\}$
is locked before any capacity-aware-detector P@50 is inspected.

The intuition is operational: at K=50 lag-1 recalibration is
beneficial (Paper 7: $\rho \approx 1.0$), so a large $\tau_{50}$
keeps the detector quiet and lag-1 used; at K=200 lag-1 is harmful
(Paper 7: $\rho \approx -0.66$), so a small $\tau_{200}$ makes the
detector fire often and revert to fixed; K=100 is intermediate.

\subsection{Justification of the $\tau_K$ Choice}

$\tau_{50} = 0.20$ is twice Paper~11's largest sweep value (0.10),
where the Paper~11 K=50 fire fraction was already 40\%. A doubling
should reduce this to near zero. $\tau_{200} = 0.02$ is Paper~11's
smallest sweep value, at which the K=200 fire fraction was 80\%
(the maximum across the Paper~11 grid). $\tau_{100} = 0.05$ is the
Paper~10 default and the midpoint of Paper~11's grid.

These three values were chosen by inspection of Paper~11's
\textit{calibration-seed} change-point decision log; the
evaluation-seed P@50 values for the cap\_aware strategy were not
inspected before locking.

\subsection{Selection Policy}

Fleet evolution is driven by HygienePrio-full under \textsf{fixed}
weights at every window for every strategy, as in Papers~7--11.
