% Section: HygieneBench Design
% Source: paper_draft_v0.1.md § 3. HygieneBench Design
% [VERIFY ACM TEMPLATE BEFORE SUBMISSION]

\section{\hygienebench Design}
\label{sec:design}

\subsection{Schema and Synthetic Generator}

\hygienebench v0.1 uses a schema with eleven entity/event tables and one anomaly
label table (Table~\ref{tab:schema}). The generator (\texttt{SyntheticHygieneGenerator})
is implemented in Python using NumPy and Pandas, with all randomness gated through
\texttt{numpy.random.default\_rng(seed)}. Entity identifiers are deterministic UUIDs
derived from \texttt{hashlib.md5(seed\_tag + index)}, ensuring reproducibility
across platforms.

\input{tables/tab_schema}

\paragraph{Structural priors.}
Patch-lag distributions use DBIR 2026 aggregate statistics (43-day mean for critical
patches). CVE severity distributions use NVD base score statistics. Telemetry
refresh cadence requirements follow CISA BOD 23-01 (14-day asset discovery, 72-hour
patch data)~\cite{cisa_bod2301_2022}. AD group-size distributions lack a
peer-reviewed published source and are modeled via disclosed assumptions (power-law
approximation) with sensitivity sweeps. All structural priors are documented in the
dataset card.

\paragraph{Conditions.}
Five telemetry conditions parameterize freshness and missingness:

\begin{itemize}[leftmargin=*]
  \item \textbf{C-BASE:} No artificial staleness; all sources current.
  \item \textbf{C-FRESH:} Elevated freshness flagging; sources verified current.
  \item \textbf{C-STALE:} 20\% of entities have heavy-stale telemetry ($>$14-day gap).
  \item \textbf{C-MISS:} One data source absent for 15\% of entities.
  \item \textbf{C-UNSUP:} C-BASE with anomaly labels withheld from the training pipeline.
\end{itemize}

Each condition is generated for three seeds (42, 137, 2024), producing 15 dataset
instances (5 conditions $\times$ 3 seeds) with $n$=1,000 users per instance.

\subsection{Anomaly Taxonomy}

\hygienebench defines twelve anomaly classes (Table~\ref{tab:taxonomy}), each
mapped to an ATT\&CK enabling condition (not a detection claim for any specific
technique). Enabling-condition mappings are annotated with a required disclaimer:
\emph{correlation with an ATT\&CK enabling condition does not imply that any
specific attack technique was executed or detected.}

\input{tables/tab_taxonomy}

\subsection{Benchmark Tasks}

Seven tasks cover the twelve anomaly classes across different entity scopes and
temporal windows (Table~\ref{tab:tasks}). Task injection counts are per dataset
instance; injection uses \texttt{AnomalyInjector(seed + 999)} to ensure a distinct
RNG stream from the generator.

\input{tables/tab_tasks}

\paragraph{Dataset splits.}
Labels are stratified 60/20/20 by anomaly class. Anomalous entities are assigned to
the test split, with normal entities split randomly across train/val/test. The split
is deterministic given the seed.
