% Section: Related Work
% Source: paper_draft_v0.1.md § 2. Related Work

\section{Related Work}
\label{sec:related}

\paragraph{Network intrusion and attack emulation benchmarks.}
The LANL Unified Host and Network Dataset~\cite{kent2015lanl} provides large-scale
enterprise network flow and authentication telemetry, but it captures network-level
events and does not model identity hygiene state (account staleness, privilege
drift) or endpoint patch posture. CICIDS~\cite{sharafaldin2018cicids} and DARPA
datasets~\cite{darpa_tc_2018} focus on network traffic classification. Mordor/Security
Datasets~\cite{rodriguez2019mordor} and BOTSv3~\cite{splunk_botsv3} provide
attack-emulation telemetry
from red-team exercises---a fundamentally different framing from hygiene-state
monitoring. None of these benchmarks includes telemetry freshness or missingness as
a controlled evaluation variable.

\paragraph{Insider threat datasets.}
The Carnegie Mellon CERT Insider Threat Dataset~\cite{glasser2013cert} includes user
behavior logs (email, file access, login) for insider-threat detection. While it
covers some identity-adjacent behaviors, it does not model endpoint patch state,
vulnerability records, or the multi-table hygiene-state structure of enterprise AD
environments.

\paragraph{Graph anomaly detection.}
The graph anomaly detection literature has produced several methods and datasets for
attributed-graph anomalies~\cite{ding2019dominant,liu2024pygod}. These approaches
typically operate on single-hop graph structure and do not model the temporal,
multi-table telemetry characteristic of enterprise security operations.

\paragraph{Commercial and proprietary platforms.}
Microsoft Defender for Identity, Entra ID Protection, Splunk UBA, Exabeam, and
Microsoft Sentinel address overlapping detection problems. They are commercial
products, not open benchmarks, and do not release datasets or evaluation
methodologies for external comparison. We make no comparison claims against these
platforms.

\paragraph{Synthetic security dataset generation.}
Synthetic generation of security telemetry has precedent in network
simulation~\cite{creech2013kdd}. \hygienebench extends this tradition to the
hygiene-state domain with documented structural priors and a reproducible seeded
generator.

\paragraph{Failure-aware and negative-result reporting.}
The practice of explicitly reporting when ML fails to outperform simpler baselines
is well-established in machine learning~\cite{sculley2018winners} but
underrepresented in security benchmark papers. \hygienebench operationalizes this
with a pre-registered $\Delta$-threshold protocol applied across all runs.
