% Section: Experimental Setup
% Source: paper_draft_v0.1.md § 4. Experimental Setup

\section{Experimental Setup}
\label{sec:setup}

\subsection{Methods}

We evaluate eight methods representing the main algorithmic families applicable
to unsupervised tabular anomaly detection under class imbalance
(Table~\ref{tab:methods}).

\input{tables/tab_methods}

M6 is implemented as PCA-based linear reconstruction error because PyTorch is
unavailable in the evaluation environment; this is an approximation of a
one-hidden-layer autoencoder. M8 is implemented using \texttt{networkx} graph features
(degree, privileged-degree, clustering coefficient) combined with Isolation
Forest rather than DOMINANT-style deep graph autoencoders~\cite{ding2019dominant},
for the same reason. Both approximations are documented. M8 is excluded from T4
and T5 by design (no meaningful graph signal for asset/patch anomalies; reported
as N/A).

\subsection{Feature Engineering}

For each task, \texttt{TaskFeatureExtractor.extract(task\_id, seed)} computes a
feature matrix from raw CSVs. Features include task-relevant identity state
attributes, temporal aggregates (e.g., 30-day login frequency, off-hours rate,
cross-segment rate), patch compliance scores, vulnerability counts, KEV exposure
counts, and telemetry freshness scores. Missing values are imputed with
training-set column means before fitting.

\subsection{Metrics and Negative-Result Protocol}

\paragraph{Primary metrics.}
Average Precision (AP) and Precision@$k$ (P@$k$) at task-specific $k$ values
(Table~\ref{tab:tasks}). AP is the standard interpolated area under the
precision-recall curve. P@$k$ is the fraction of true anomalies in the top-$k$
ranked entities---the operationally relevant metric for SOC review budgets.

\paragraph{Secondary metrics.}
Recall@$k$ (R@$k$), False Positive Burden (FPB $= 1 - $P@$k$), and AP stability
($1 - \text{CV}$ across seeds).

\paragraph{Pre-registered failure protocol.}
A (condition, task, method) configuration is flagged as a \emph{negative result}
($\blacktriangleright$) if:
\begin{equation}
\begin{aligned}
  &\text{AP}(\text{method}) - \text{AP}(\text{M1}) < 0.05 \\
  &\quad\textbf{and}\quad
  \text{P@}k(\text{method}) - \text{P@}k(\text{M1}) < 0.05
\end{aligned}
\label{eq:failure}
\end{equation}
in at least $\lceil 2/3 \times n_{\text{seeds}} \rceil = 2$ of 3 seeds.
Flagged configurations are reported in full and are not filtered.
This protocol was pre-registered prior to examining any results.
