\section{Problem Formulation}
\label{sec:problem}

\subsection{Setting (Inherited)}

EEHDA synthetic fleet, scorer Eq.~(\ref{eq:hp}), multi-window
simulator, $K \in \{50, 100, 200\}$, $\lambda = 3$, six windows,
25 evaluation seeds, 5 calibration seeds. Inherited from
Papers~4--12.

\subsection{Six Strategies}

\begin{description}
\item[\textsf{fixed}] Paper 4 weights, no refit.
\item[\textsf{lag1}] Paper 7 baseline lag-1 grid search.
\item[\textsf{cap\_aware}] Paper 12 capacity-aware ($\tau_K = \{50:
0.20, 100: 0.05, 200: 0.02\}$), included as a control.
\item[\textsf{cusum}] CUSUM($k = 0.04, h = 0.10$) over $|\Delta_w|$.
\item[\textsf{gated}] Static rule ($K \leq 100 \to$ lag1; $K \geq
200 \to$ fixed).
\item[\textsf{offline}] Paper 7 ceiling at window $w$.
\end{description}

\subsection{Pre-Registered Hypotheses}

\begin{description}
\item[H1] \textsf{cusum} reaches the joint feasibility region:
worst K=200 cusum--fix $\geq -0.01$, cell-mean K=50 cusum--lag1
$\geq -0.02$, cell-mean K=100 cusum--lag1 $\geq -0.02$.
\item[H2] \textsf{cusum} K=200 cell-mean $\geq$ \textsf{gated}
K=200 cell-mean $+ 0.01$. \textit{CUSUM beats the static gate at
the high-capacity extreme by an operationally meaningful margin.}
\item[H3] \textsf{cusum} K=200 fire fraction $<$ \textsf{cap\_aware}
K=200 fire fraction (selective firing).
\item[H4] \textsf{cusum} K=200 cell-mean $\geq$ \textsf{cap\_aware}
K=200 cell-mean $- 0.01$ (CUSUM does not lose meaningfully relative
to the cap\_aware control).
\end{description}

\subsection{Stop Rules}

If H2 is rejected, the abstract leads with ``CUSUM also collapses to
static gate'' before the discussion is drafted. If H1 is rejected,
feasibility precedence applies and the abstract leads with the
infeasibility rather than the H2 improvement claim.
