\section{Methodology}

\subsection{Scorer and Adaptive Procedure (Inherited)}

The HygienePrio scorer Eq.~(\ref{eq:hp}) and HRS components are
inherited verbatim from Paper~4~\cite{paper4hygieneprio}. The adaptive
change-point procedure is identical to Paper~10~\cite{paper10adaptive}
except $\tau$ is now a swept parameter:

\begin{equation}
\begin{aligned}
S(h,c) =\;& \alpha\,\mathrm{EPSS}(c) + \beta\,\mathrm{HRS}(h) \\
          & + \gamma\,\mathrm{KEV\_recency}(c) \\
          & + \delta\,\bigl(\mathrm{EPSS}(c) \cdot \mathrm{HRS}(h)\bigr).
\end{aligned}
\label{eq:hp}
\end{equation}

At window $w \geq 2$ the detector computes the calibration-target
shift $\Delta_w$ (Paper~10~\S5.2) and fires if $|\Delta_w| \geq \tau$.
On fire, \textsf{adaptive}$(\tau)$ uses \textsf{fixed} weights;
otherwise it uses the lag-1-fit weights. \textsf{lag1},
\textsf{offline}, and \textsf{gated} are unchanged.

\subsection{Efficiency Observation}

$\Delta_w$, the lag-1-fit weights, and the offline-peek weights are
all $\tau$-independent. We compute them once per (cell, window) and
reuse them across all five $\tau$ values, so the per-$\tau$ marginal
cost is only the per-strategy re-scoring of the 25 evaluation seeds
at each window (much cheaper than the 108-point grid search).
The total runtime is therefore approximately the same as Paper~10's
single-$\tau$ run.

\subsection{Per-$\tau$ Metrics}

For each $\tau \in$ grid:
\begin{itemize}
\item Worst per-window $\Delta^{\textsf{adaptive}-\textsf{fixed}}_{K=200}$:
the minimum over $w \in \{2, \ldots, 6\}$ of the cell-mean delta.
\item Cell-mean $\Delta^{\textsf{adaptive}-\textsf{lag1}}_{K=50}$:
mean over $w \geq 2$.
\item Firing fraction per cell: fraction of post-W1 windows where
the detector fired.
\item Cell-mean P@50 per (cell, strategy) for all five strategies.
\end{itemize}
