Prior work on rolling-history online calibration of the HygienePrio
scorer~\cite{paper7online} found that lag-1 recalibration recovers the
offline-peek calibration ceiling at moderate capacity (per-cell
recovery ratio $\rho \in \{1.04, 0.99\}$ at $K \in \{50, 100\}$,
$\lambda = 3$) but \textit{harms} performance at $K = 200$
($\rho = -0.66$), and named multi-window-history smoothing as the
natural candidate fix. This paper evaluates that fix in a
pre-registered 2{,}250-row five-strategy comparison: \textsf{fixed}
(the prior HygienePrio weights~\cite{paper4hygieneprio}), \textsf{lag1}
(the one-window-lag baseline of~\cite{paper7online}), \textsf{trail3}
(equal-weight 3-window trailing mean), \textsf{ewma3}
(exponentially-weighted 3-window mean, $\alpha = 0.6$), and
\textsf{offline} (the offline-peek ceiling of~\cite{paper7online}).

\textbf{All four pre-registered hypotheses are rejected, and the
direction of rejection is the contribution.} Multi-window smoothing
does \textit{not} reverse the high-capacity hazard --- it makes the
hazard substantially worse. At $K = 100$, EWMA-3's cell-mean recovery
ratio is $-1.37$ (versus lag-1's $+0.99$); at $K = 200$ it is $-0.94$
(versus lag-1's $-0.66$); at $K = 50$ the matched-capacity moderate
regime, EWMA-3 \textit{also} underperforms lag-1 ($\rho = 0.53$
versus $1.04$).

The mechanism is the inverse of the naive smoothing-helps intuition.
At high capacity the fleet's distribution at window $w$ has shifted
substantially from window $w - 3$, $w - 2$, $w - 1$; weighting all
three past windows in the calibration target pulls the selected
weights \textit{further} from the appropriate-for-window-$w$ optimum,
not closer to it. The hazard is monotone in history length: less
history is better when the rate of distributional change is fast.

The operational recommendation that emerges is sharper than that of~\cite{paper7online}:
deployable online recalibration in this setting should use the
shortest possible history (lag-1 at most) and should be turned off
entirely at high capacity. Future work is needed on more sophisticated
adaptive procedures (change-point detection, Bayesian update with
forgetting factor) that can identify when smoothing is locally
appropriate. All results bounded to the synthetic EEHDA evaluation
context; external validation on real fleet telemetry with longitudinal
exploitation outcome data is required before deployment.
