\section{Introduction}

Papers~5--8 of the VulnPrio research sequence all bound their findings
to a single trajectory regime --- the one in which HygienePrio-full's
top-$K$ selection drives fleet evolution at every window. The choice was
deliberate and pre-registered: when each method drives its own
counterfactual trajectory, the resulting per-method residual backlogs
differ, the per-window positive sets are computed against different
states, and direct cross-method P@50 comparisons become
non-identifiable. The HygienePrio-driven trajectory was the
identifiability-preserving compromise.

Paper~6~\cite{paper6capacity} additionally reported that HygienePrio-full's
W6 P@50 collapses at $K \in \{100, 200\}$ on this baseline trajectory and
named the mechanism ``high-HRS-tail exhaustion'': HygienePrio-full
preferentially remediates high-HRS hosts, those hosts exit the upper
HRS tail, and HygienePrio's discriminative signal degrades. The
mechanism is, by construction, induced by HygienePrio's own selection.

This paper asks the inevitable follow-up. \textit{If the collapse is
induced by HygienePrio's selection draining the HRS tail, what happens
when a different method drives the trajectory?} A capacity-$K = 200$
deployment that uses HygienePrio for scoring but, say, CVSS-only for
selection (or vice versa) does not exhibit the recursive
HRS-tail-exhaustion mechanism. The Paper~6 collapse should not appear.

We pre-registered three hypotheses
(\texttt{paper9/design/PAPER9\_PROTOCOL.md}, locked 2026-06-05 before
any self-trajectory result was inspected) and ran a 7{,}500-row
evaluation that fills in all five trajectory-driver columns of the
P@50 grid at $K \in \{50, 200\}$, $\lambda = 3$. The results retroactively
reframe Papers~5--8.

\subsection{Contributions}

\begin{itemize}
\item \textbf{C1 --- Trajectory grid.} The first pre-registered
trajectory-stratified evaluation of HygienePrio: 5 driver methods
$\times$ 5 scoring methods $\times$ 2 cells $\times$ 25 seeds
$\times$ 6 windows = 7{,}500 rows.

\item \textbf{C2 --- The collapse is selection-induced.} Paper~6's
W6 P@50 collapse of HygienePrio-full from $\sim 0.5$ at $K = 50$ to
$0.062$--$0.075$ at $K = 200$ is reproduced under the
HygienePrio-driven trajectory. Under any HRS-blind driver ---
CVSS-only, HRS-only, or Random --- HygienePrio's W6 P@50 at $K = 200$
sits between $0.701$ and $0.713$. The collapse mechanism is recursive,
not intrinsic.

\item \textbf{C3 --- EPSS-self-driven is the deepest sink.} At
$K = 200$ under EPSS-only-driven trajectory, every scorer's W6 P@50
collapses to $0.001$--$0.012$. EPSS-only's selection so aggressively
remediates the high-EPSS tail that the binary ground-truth positive
set is itself exhausted by W6. The trajectory effect is shared by
EPSS-only and HygienePrio-full but for a different mechanism.

\item \textbf{C4 --- Per-pair dominance is trajectory-conditional.}
At $K = 50$, HygienePrio-full $>$ EPSS-only on $100\%$ of (seed,
window) pairs under every non-trivial driver. At $K = 200$ under
EPSS-only's own driver, the fraction collapses to $0.393$
(where both methods are near zero together). At $K = 200$ under
HRS-only, CVSS-only, or Random drivers, the fraction is $1.000$.
Paper~5's headline $96\%$ statistic is preserved at moderate
capacity and at HRS-blind drivers; it does not survive at the
EPSS-self-driven high-capacity corner.

\item \textbf{C5 --- Sharpened operational reading.} HygienePrio's
absolute floor at high capacity is intact whenever the deploying
organisation does not also use HygienePrio's selection policy.
The Paper~6 H4 collapse is a property of recursive deployment
(score-and-drive simultaneously), not of hygiene-augmented scoring
as a method. A team using HygienePrio for scoring should expect
the high absolute P@50 reported in Paper~5--7 across capacity
regimes, provided some other policy drives the patching queue.
\end{itemize}

\subsection{Relationship to Prior Papers}

This paper is the ninth in the VulnPrio sequence. Papers~5--8
identified a number of regime-specific findings (temporal stability,
capacity-induced collapse, deployable calibration, smoothing
falsification); the present paper shows that the most prominent of
those findings --- Paper~6's H4 high-capacity collapse --- is partly
a closed-loop artefact. The other findings (Paper~5 per-pair dominance,
Paper~7's lag-1 calibration in moderate-$K$, Paper~8's smoothing
penalty) are unchanged but should be cited together with the
trajectory column they were measured on.
