\section{Problem Formulation}
\label{sec:problem}

\subsection{Setting (Inherited)}

The synthetic EEHDA fleet, scorer (\S5.1), HRS components, and
multi-window simulator follow~\cite{paper4hygieneprio,paper5temporal,paper6capacity,paper7online}.
Capacity $K \in \{50, 100, 200\}$ and arrival rate $\lambda = 3$
are fixed to match the evaluation of~\cite{paper7online}; the only
quantity varied in this paper is the calibration strategy.

\subsection{Five Calibration Strategies}

At window $w$, the scorer uses weights $(\alpha, \beta, \gamma, \delta)$
determined by:

\begin{description}
\item[\textsf{fixed}] HygienePrio weights at every window. No refit.
\item[\textsf{lag1}] At $w = 1$, weights are \textsf{fixed}; at
$w \geq 2$, grid-search to maximise mean P@50 on the five calibration
seeds at window $w - 1$. (the prior online-calibration evaluation baseline.)
\item[\textsf{trail3}] At $w = 1$, weights are \textsf{fixed}; at
$w \geq 2$, grid-search to maximise the equal-weight mean of
per-window mean P@50 across windows $\max(1, w - 3), \ldots, w - 1$.
At $w = 2$ this reduces to \textsf{lag1}; at $w \geq 4$ this averages
exactly three past windows.
\item[\textsf{ewma3}] Same set of past windows as \textsf{trail3} but
with geometric weights $\alpha^i$, $i = 0, 1, 2, \ldots$ counting back
from the most recent past window. Pre-registered $\alpha = 0.6$.
\item[\textsf{offline}] Peek at window $w$ on the calibration seeds.
(Upper-bound ceiling.)
\end{description}

The grid is identical to the prior online-calibration evaluation (108 points).

\subsection{Ground Truth and Metric}

Inherited from the prior multi-window evaluations: (EPSS $> 0.10$) $\wedge$ (HRS $>$ 75th
percentile recomputed per window), P@50 measured against the resulting
positive set.

\subsection{Pre-Registered Hypotheses}

\begin{description}
\item[H1] At $K = 200$, \textsf{ewma3} mean P@50 $\geq$ \textsf{fixed}
at every $w \geq 2$ (within $-0.01$ tolerance). \textit{No hazard at
high capacity.}
\item[H2] At $K \in \{50, 100\}$, $|\textsf{ewma3} - \textsf{lag1}|
\leq 0.02$ at every $w \geq 2$. \textit{Smoothing does not break
moderate-capacity recovery.}
\item[H3] $|\textsf{ewma3} - \textsf{trail3}| \leq 0.02$ at every
cell-window. \textit{Smoothing-strategy choice is second-order.}
\item[H4] At $K = 200$, EWMA-3 cell-mean recovery ratio $\bar\rho
\geq 0.5$. \textit{EWMA achieves substantial offline-ceiling recovery.}
\end{description}

Decision rules and stop rules are pre-registered in the protocol archived with the reproducibility artifact.
