\section{Methodology}

\subsection{Scorer (Inherited)}

The HygienePrio scorer Eq.~(\ref{eq:hp}) and HRS components are
inherited verbatim from Paper~4~\cite{paper4hygieneprio} and used in
Papers~5--7:
\begin{equation}
\begin{aligned}
S(h,c) =\;& \alpha\,\mathrm{EPSS}(c) + \beta\,\mathrm{HRS}(h) \\
          & + \gamma\,\mathrm{KEV\_recency}(c) \\
          & + \delta\,\bigl(\mathrm{EPSS}(c) \cdot \mathrm{HRS}(h)\bigr).
\end{aligned}
\label{eq:hp}
\end{equation}
HRS combines patch posture (0.50), AD exposure (0.30), and telemetry
freshness (0.20). Only the four scorer weights $(\alpha, \beta, \gamma,
\delta)$ are subject to recalibration.

\subsection{Multi-History Grid Search}

At window $w \geq 2$ and for a calibration strategy with history set
$H \subseteq \{1, \ldots, w-1\}$ and per-history-window weights
$\{u_i\}_{i \in H}$:
\begin{enumerate}
\item For each of the 108 grid points $g = (\alpha, \beta, \gamma,
\delta)$:
\begin{enumerate}
\item For each $i \in H$, compute the mean P@50 across the five
calibration seeds at window $i$ when scored with weights $g$.
\item Take the weighted mean across history windows
$\bar{p}(g) = \sum_{i \in H} u_i\, p_i(g) / \sum_i u_i$.
\end{enumerate}
\item Select $g^\star = \arg\max_g \bar{p}(g)$; ties broken lexicographically.
\item Apply $g^\star$ to each of the 25 evaluation seeds at window $w$
and record the seed's P@50.
\end{enumerate}

\textsf{lag1}, \textsf{trail3}, and \textsf{ewma3} instantiate this
with different $(H, \{u_i\})$:

\begin{itemize}
\item \textsf{lag1}: $H = \{w-1\}$, single uniform weight.
\item \textsf{trail3}: $H = \{\max(1, w-3), \ldots, w-1\}$, equal weights.
\item \textsf{ewma3}: $H = \{\max(1, w-3), \ldots, w-1\}$, geometric
weights $u_i = \eta^{(w-1)-i}$ with $\eta = 0.6$, so the most recent
past window receives weight $\eta^0 = 1$ and older windows receive
$0.6, 0.36, \ldots$.
\end{itemize}

\subsection{Fleet-State Evolution}

Identical to Paper~7: HygienePrio-full under \textsf{fixed} weights
drives the top-$K$ selection at every window, producing the same
trajectory for all strategies. The calibration strategy affects only
the scoring weights, not the fleet evolution. The selection-policy
coupling threat is restated in \S\ref{sec:threats}.

\subsection{Recovery Ratio}

For each (cell, window) with $w \geq 2$ and a positive offline-fixed
gap, we report:
\begin{equation}
\rho_{K, w}^{\text{ewma}} =
\frac{\text{P@50}^{\textsf{ewma3}}_{K, w} - \text{P@50}^{\textsf{fixed}}_{K, w}}
     {\text{P@50}^{\textsf{offline}}_{K, w} - \text{P@50}^{\textsf{fixed}}_{K, w}}.
\end{equation}
$\rho \approx 1$ matches the offline ceiling; $\rho < 0$ is a hazard.
The ratio is reported only where the offline--fixed gap exceeds the
pre-registered threshold of $0.01$
($\text{P@50}^{\textsf{offline}} - \text{P@50}^{\textsf{fixed}} > 0.01$);
windows below the threshold are excluded as numerically unstable
denominators. The cell-mean across $w \geq 2$ is
$\bar\rho_K^{\text{ewma}}$.
