\section{Experimental Setup}

\subsection{Pre-Registration}

The cell grid, five-strategy definition, hypotheses H1--H4, decision
rules, and stop rules in \texttt{paper8/design/PAPER8\_PROTOCOL.md}
were locked on 2026-06-04 before any multi-history-calibration result
was computed.

\subsection{Execution}

For each $K \in \{50, 100, 200\}$:
\begin{enumerate}
\item Cache per-window $(\text{pairs}_w, \text{HRS}_w)$ states for the
five calibration seeds (driving evolution with fixed-weight HygienePrio-full).
\item Cache per-window states for the 25 evaluation seeds (same trajectory policy).
\item For each window $w = 1, \ldots, 6$, determine each strategy's
weights as in \S5.2, score every evaluation seed at $w$ with each
strategy's weights, and record one row per (seed, window, strategy).
\end{enumerate}

\subsection{Statistical Reporting}

Cell-mean point estimates are means across 25 evaluation seeds. 95\%
confidence intervals are percentile bootstrap (10{,}000 resamples)~\cite{efron1994introduction}.
No null-hypothesis significance tests are reported; hypothesis decisions
follow the pre-registered tolerance thresholds.

\subsection{Reproducibility}

From \texttt{paper8/}:
{\small\begin{verbatim}
PYTHONPATH=src python3 src/run_multi_history.py
PYTHONPATH=src python3 src/analyze.py
PYTHONPATH=src python3 src/make_figures.py
\end{verbatim}}
The runner re-uses Paper~5's window simulator and Paper~4's scorer
via \texttt{sys.path} injection. Determinism inherited from Paper~5's
per-(seed, window, step) RNG seeding.
