\section{Discussion}

\subsection{What This Paper Changes About Paper~6}

Paper~6~\cite{paper6capacity} reported HygienePrio's H4 absolute-floor
collapse at $K \in \{100, 200\}$ as a property of hygiene-augmented
scoring under high capacity. The present paper shows the collapse is
substantially a property of \textit{recursive deployment}: when the same
policy that scores also drives selection, that policy preferentially
remediates the host-tail it depends on, and that tail exhausts.
Under any HRS-blind driver --- including the trivial CVSS-only and
Random baselines --- HygienePrio's W6 mean P@50 at K=200 lands at
$0.701$--$0.713$, an order of magnitude above the self-trajectory
number.

The operational corollary is sharp. A team that uses HygienePrio for
scoring and lets some \textit{other} policy --- for example, a
ticketing system, a compliance-driven schedule, or a CVSS-based
queue --- determine which pairs are actually patched first will not
experience the Paper~6 collapse. The collapse is a closed-loop
artefact, not a property of hygiene-augmented scoring as a method.

\subsection{Why EPSS-Self-Driven Destroys Everything}

The K=200, $T_{\mathrm{EPSS}}$ column of Table~\ref{tab:w6grid} contains
the most extreme cell in the grid. Five W6 P@50 values, all in
$[0.000, 0.012]$. The mechanism is ground-truth-set exhaustion:
EPSS-only's selection at K=200 removes the high-EPSS tail so fast that
the binary positive condition (EPSS $> 0.10$) is satisfied by an
essentially empty residual backlog. Once the positive set is empty,
P@50 is mechanically zero regardless of which scorer is being
evaluated --- you cannot rank a non-existent positive.

This is a stronger version of the Paper~6 capacity collapse story.
Paper~6 documented that HygienePrio drains the HRS tail; the present
paper shows that EPSS-only drains its own EPSS tail to a literal zero
floor. Both are recursive-deployment artefacts; neither is an
intrinsic scoring failure.

\subsection{What Paper~5's 96\% Per-Pair Dominance Actually Means}

Paper~5 reported that HygienePrio-full $>$ EPSS-only at P@50 in
$96.0\%$ of (cell, seed, window) triples under the (then-implicit)
HygienePrio-driven trajectory. The present paper finds that this
statistic survives at $K = 50$ under every driver (always $1.000$),
survives at $K = 200$ under HRS, CVSS, and Random drivers
($1.000$), partially survives at $K = 200$ under HygienePrio's own
driver ($0.800$), and \textit{does not} survive at $K = 200$ under
the EPSS-only driver ($0.393$). The interpretation: per-pair
dominance is a robust property of HygienePrio under any
HRS-blind selection, including the natural baselines an operations
team would deploy if not using HygienePrio's score for selection.
Under the EPSS-self-driven regime both methods collapse together,
and the comparison becomes degenerate.

\subsection{What Paper~6's H4 Rejection Means After This Paper}

Paper~6's H4 rejection now reads as follows. HygienePrio-full's
absolute W6 P@50 at $K \geq 100$ is degraded \textit{only} when
HygienePrio also drives the trajectory. The mechanism is recursive
HRS-tail exhaustion. On any non-HP driver, the absolute floor is
intact at the Paper~5 level ($\sim 0.5$ or higher). The original
H4 hypothesis ``HygienePrio retains $\geq 0.4$ at every cell'' is
\textit{re-supportable} under the qualified statement ``on every cell,
on at least one non-HP driver''. We do not formally re-test Paper~6
H4 here because doing so would constitute hypothesising after results
known (HARKing); we report the observation honestly and leave a
new pre-registered H4-style restatement to future work.

\subsection{Why the Trajectory Effect is Asymmetric Across Scorers}

The trajectory-effect range $\Delta^{\mathrm{traj}}_m$ is largest for
HP-full and EPSS-only and smallest for CVSS-only and Random. The
asymmetry has a clean structural interpretation: a scorer's W6
performance depends on whether the driver preferentially drained the
ground-truth-positive tail that the scorer relies on. HP-full relies
on the HRS upper tail; HP-driven drains it. EPSS-only relies on the
EPSS upper tail; EPSS-driven drains it. CVSS-only relies on the CVSS
upper tail (which is not part of the ground-truth condition) so no
driver in the grid preferentially drains it. Random relies on no
signal. The two scorers most sensitive to trajectory are the two
scorers whose ranking is most aligned with the ground-truth positive
set --- which is the same property that makes them the strongest
scorers in the first place.

\subsection{Operational Recommendations}

Sharpened from Papers~5--8:
\begin{itemize}
\item Use HygienePrio for scoring across all studied capacity
regimes; its per-pair dominance over EPSS-only is preserved
whenever the deploying organisation does not also use HygienePrio
as the selection policy at high capacity.
\item Do not let HygienePrio be both the scorer and the queue-driving
policy at $K \geq 100$. Either (i) decouple --- use HygienePrio
for ranking but let another policy (ticketing system, CVSS queue,
human triage) drive the patching cycle, or (ii) accept the Paper~6
H4-style collapse as the cost of full automation.
\item Do not deploy EPSS-only as both scorer and selection policy at
high capacity. EPSS-self-driven at K=200 produces a literal zero
floor by W6.
\end{itemize}

\subsection{Relationship to the Research Sequence}

This paper closes a gap that Papers~5--8 explicitly bounded but did
not measure. The cumulative arc is unchanged in spirit: hygiene
augmentation helps prioritization. But the headline ``HygienePrio
holds up across regimes'' is now sharper. It holds up across regimes
\textit{except} when HygienePrio itself is the recursive driver of
fleet evolution at high capacity. That last condition is operationally
controllable, and the recommendation is to control it.
