\section{Threats to Validity}
\label{sec:threats}

The threats taxonomy follows Wohlin et al.~\cite{wohlin2012experimentation}.

\textbf{Conclusion validity.} The evaluation comprises 2{,}250
(cell, seed, window, strategy) observations summarised with 95\%
percentile bootstrap CIs (10{,}000 resamples). The hypothesis decision
rules are based on per-cell-window deltas; small per-cell-window
differences ($|\Delta| \leq 0.02$) are within the bootstrap noise band
and we report them as ties rather than as substantive effects.

\textbf{Internal validity.}

\textit{(i) Selection-policy coupling.} As in the prior multi-window evaluations, fleet
evolution is driven by HygienePrio-full under the \textsf{fixed}
weights at every window. All five strategies score against the same
evolving backlog, isolating the calibration-weights effect. In a real
closed-loop deployment the selection policy would also be recalibrated
and the trajectory would diverge across strategies; this is a known
limitation shared with the prior online-calibration evaluation.

\textit{(ii) EWMA $\alpha$ is pre-registered, not tuned.} We fixed
$\alpha = 0.6$ in the protocol to avoid post-hoc tuning. Different
$\alpha$ values would produce different smoothing trade-offs;
sensitivity sweeps over $\alpha$ are deferred to future work.

\textit{(iii) Trailing history $H = 3$ is fixed.} Longer trailing
histories ($H = 4$ or $H = 6$) might further smooth at high $K$ but
add more lag; $H = 3$ was chosen as the smallest history that
distinguishes from \textsf{lag1} while keeping a reasonable
effective horizon.

\textbf{Construct validity.} P@50 at $K = 200$ becomes noisy at late
windows due to small positive-set sizes. The K=200 hypothesis decisions
therefore weight earlier-window results (W2--W4) more heavily through
the cell-mean recovery ratio.

\textbf{External validity.} Inherited from the prior HygienePrio-line work~\cite{paper4hygieneprio,paper5temporal,paper6capacity,paper7online}: synthetic
EEHDA structural priors, 14-day window, 0.15 patch debt reduction,
0.02 EPSS random walk, 8\% KEV prevalence. Real fleets with different
rate-of-distributional-shift dynamics would produce different
$(\alpha, H)$ optima; the qualitative finding --- whether smoothing
helps at high capacity --- is more robust than the specific parameter
choices.
