\section{Related Work}

\textbf{Lag-1 online calibration baseline.}
Paper~7~\cite{paper7online} introduced the rolling-history grid-search
recalibration procedure and reported the capacity-conditional hazard
that motivates this paper. The present sweep inherits Paper~7's
\textsf{fixed}/\textsf{lag1}/\textsf{offline} strategies and adds the
two smoothing variants.

\textbf{High-capacity collapse.} Paper~6~\cite{paper6capacity}
identified the high-capacity regime where HygienePrio-full collapses
even with fixed weights. The present paper does not attempt to rescue
the absolute floor (that question is taken up in the future-work
section); instead it asks whether a smoothed online recalibration
procedure can match or exceed the fixed-weight baseline at the
collapse cells.

\textbf{Exponential smoothing.}
The EWMA estimator dates back at least to Holt's seasonal-forecasting
work~\cite{huang2024ewma}; in machine-learning settings it appears
under the name ``geometric averaging'' as a low-variance bias-bearing
substitute for sliding-window means. The use here --- weighting a
finite past history of grid-search calibration scores --- is a direct
adaptation; no novel estimator is claimed.

\textbf{Multi-paper sequence.}
HygieneBench~\cite{paper3hygienebench}, HygienePrio~\cite{paper4hygieneprio},
Temporal Stability~\cite{paper5temporal}, Capacity-Indexed Decay~\cite{paper6capacity},
and Online Calibration~\cite{paper7online} together define the
methodological substrate within which this paper sits. This paper
extends the calibration-strategy dimension by one step (single-lag $\to$
finite-history weighted aggregation).

\textbf{Policy mandates.} CISA BOD~22-01~\cite{cisa2021bod2201},
23-01~\cite{cisa2022bod2301}, NIST SP~800-40 Rev.~4~\cite{nist2022sp80040r4},
and the 2026 DBIR~\cite{verizon2026dbir} establish the operational
scheduling regime under which any deployable recalibration procedure
must operate.
